### 2024-05-02 Final_Report/paper.tex
abstract started

% TODO fill in your paper title
\newcommand{\PaperTitle}{A Comparative Analysis of Machine Learning Algorithms for Website Traffic Classification from Network Packets }
% TODO fill in your paper number when you get it
\newcommand{\PaperNumber}{XXX}

\documentclass[10pt,sigconf,letterpaper,nonacm]{acmart}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is the preamble; include packages as you see fit.
% Here are a few recommendations:
% \usepackage{color}
% \usepackage{graphicx}
% \usepackage[labelformat=simple]{subcaption}
% \usepackage{xspace}
% \usepackage{multirow}
% \usepackage[ruled,vlined]{algorithm2e}
% \usepackage{ulem}
% \normalem

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\PaperTitle}

\author{XXX}
\email{xxx@xxx.com}
\author{YYY}
\email{yyy@yyy.com}
\affiliation{
  \institution{William \& Mary}
  \city{Williamsburg}
  \state{Virginia}
  \country{USA}
}

\begin{abstract}
Accurately Identifying web traffic destination and origins is crucial for the efficiency of a network. This project explores the potential of machine learning in reference to web traffic classification based on the 
analysis of network packets. 
We monitored and analyzed web traffic data from ChatGPT, Blackboard, and Linkedin, with the objective 
of building models which will be able to predict the web traffic origin of a specific packet. The collection of data was performed
using wireshark, then the data was reformatted to eliminate bias and get more accurate results.
Using the collected data we then trained four models which had varying levels of accuracy, Logistic Regression (56\%), 
K-Nearest Neighbors (77\%), Random Forest (78\%), and finally a neural
network (80\%). This project shows the importance of machine learning within the field of 
network traffic analysis as automaton is much more efficient and precise compared to manually
examining web traffic, especially in a scale as large as the internet.

\end{abstract}

\keywords{Idk what to put for keywords}

\maketitle

\section{Introduction}

\section{Proposed Method}

\section{Evaluation}

\section{Discussion \& Future Work}

\section{Conclusion}

% Note from the CFP that this section must include a statement about
% ethical issues; papers that do not include such a statement may be
% rejected.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% We're in the endgame now

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\end{document}

### 2024-05-02 KNN.py

@@ -60,7 +60,6 @@ def convertWireSharkData(chatGPTcsv,blackboardcsv, linkedIncsv, sizeOfDataFrame 
     linkedIn = resample(linkedIn,replace=False, n_samples=sampleSize,random_state=42)
     chatGPT = resample(chatGPT,replace=False, n_samples=sampleSize,random_state=42)
 
-
     chatGPT["Website"] = "ChatGPT"
     blackboard["Website"] = "Blackboard"
     linkedIn["Website"] = "Linkedin"
@@ -162,17 +161,15 @@ def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
     return confusionMatrix,accuracy,cMatrix
 
 
-    
-    
 
 # we can check what the actual predictions were and see how accurate our model is 
 # print(testWMdata)
 
 
-
 model = trainData()
 plot,modelAccuracy,cmatrix = testWMData("lakeData/test/chatgptTestData.csv", "lakeData/test/blackboardTestData.csv", "lakeData/test/linkedinTestData.csv",model)
 print(plot)
+
 
 
 

### 2024-05-02 LogReg.py

@@ -103,11 +103,11 @@ print(compare_classes(ytest, y_pred))
 
 # print(f"---------------------------Test Data------------------------------------")
 
-# WMdata = convertWireSharkData("lakeData/test/chatgptTestData.csv", "lakeData/test/blackboardTestData.csv", "lakeData/test/linkedinTestData.csv")
-# actualClasses = WMdata["Website"]
-# testData = WMdata.drop("Website", axis = 1)
-# predictedClasses = logistic_model.predict(testData)
-# confusionMatrix, accuracy = compare_classes(actualClasses,predictedClasses)
-# print(confusionMatrix,accuracy)
+WMdata = convertWireSharkData("lakeData/test/chatgptTestData.csv", "lakeData/test/blackboardTestData.csv", "lakeData/test/linkedinTestData.csv")
+actualClasses = WMdata["Website"]
+testData = WMdata.drop("Website", axis = 1)
+predictedClasses = logistic_model.predict(testData)
+confusionMatrix, accuracy = compare_classes(actualClasses,predictedClasses)
+print(confusionMatrix,accuracy)
 
 

### 2024-05-02 Final_Report/paper.tex
Added keywords and names to paper

@@
 
-\author{XXX}
-\email{xxx@xxx.com}
-\author{YYY}
-\email{yyy@yyy.com}
+\author{Matthew Berthoud, Lake Bradford, Justin Cresent, Will Katabian}
 \affiliation{
@@
 network traffic analysis as automaton is much more efficient and precise compared to manually
-examining web traffic, especially in a scale as large as the internet.
+examining web traffic, especially in a scale as large as the internet. One example of our project's significance is that this can be crucial data analysis 
+for network administrators and security professionals, whom would examine the network for malicious traffic.
 
@@
 
-\keywords{Idk what to put for keywords}
+\keywords{Network Traffic, Machine Learning, Web Traffic Classification, Network Packets, Data Analysis, Neural Networks, Random Forest, K-Nearest Neighbors, Logistic Regression}
 

### 2024-05-02 Final_Report/paper.tex
Added intro and some references in.

@@
 \section{Introduction}
+The ability to monitor and analyze network traffic is crucial for the efficiency and security of a network \cite{10.1145/2388576.2388608}. 
+It helps to manage the overall network performance, detect and prevent malicious activities, and ensure the network is operating as intended.
+The present day internet is composed of a vast variety of diverse web traffic, of which requires a more sophisticated approach to analyze and classify network traffic.\cite{10.5555/3432601.3432608}
+This project investigates a variety of machine learning algorithms to see which most accurately and effectively classify web traffic based on data from a set of captured network packets.
+
+  Traffic classification is very significant in practice, if done accurately and effectively \cite{10.1109/TNET.2014.2320577}.
+For reasons mentioned previously, the observed capabilities of this and other projects
+  can be crucial for network administrators and security professionals, whom would examine the network for malicious traffic.
+
+  For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and Linkedin.
+These sets were then merged into a single dataset, which was then split into training and testing sets.
+  Three models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.
+
+  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization along with cross-validation, and computing accuracy and Macro F1 scores.
+The results showed that the Neural Network model
+  acheived the highest accuracy of $80\%$ and Macro F1 score of BLANK. %%TODO fill in the score.%%
+  These scores show the model's ability to accurately classify the selected websites based on captured network packet data.
+
+  Overall, the significance of this project is seen in its use of Machine Learning and the extensions of these applications into the discipline of network traffic analysis.
+This practice has potential to be utilized in real-world applications, and many sources
+  proving it already is \cite{10.5555/3432601.3432608}.
 
@@
 \bibliography{refs}
+\cite{10.1145/2388576.2388608}
+\cite{10.5555/3432601.3432608}
+\cite{10.1109/TNET.2014.2320577}
+\cite{scikit-learn}
 

### 2024-05-02 Final_Report/paper.tex
Added in some subsections and descriptioons for sections 2 and 3.

@@
 \section{Proposed Method}
+This section presents the methodology for how this project goes about capturing network packet data, analyzing the data, and classifying it based on its website of origin.
 
+\subsection{Capturing Data}
+\subsection{Data Preparation and Processing}
+\subsection{Employed models}
 \section{Evaluation}
+This section comprehensively evaluates our models and their performance on the dataset and validating sets.
+\subsection{Dataset}
 

### 2024-05-02 Final_Report/paper.tex
Added subsections to sections 3 and 4
punc error

@@
 It helps to manage the overall network performance, detect and prevent malicious activities, and ensure the network is operating as intended.
-The present day internet is composed of a vast variety of diverse web traffic, of which requires a more sophisticated approach to analyze and classify network traffic.\cite{10.5555/3432601.3432608}
+The present day internet is composed of a vast variety of diverse web traffic, of which requires a more sophisticated approach to analyze and classify network traffic\cite{10.5555/3432601.3432608}.
 This project investigates a variety of machine learning algorithms to see which most accurately and effectively classify web traffic based on data from a set of captured network packets.
@@
 This section comprehensively evaluates our models and their performance on the dataset and validating sets.
+Later, goes on to determine the model which best classified our selected websites based on network packet data.
 \subsection{Dataset}
+\subsection{Model Evaluation}
+\subsection{Model Comparison and Evaluation Results}
 
 \section{Discussion \& Future Work}
+\subsection{Analysis of Results}
+\subsection{Future Work}
 

### 2024-05-02 Final_Report/paper.tex
Fixed intro mistakes

@@
 These sets were then merged into a single dataset, which was then split into training and testing sets.
-  Three models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.
+  Four models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.
 
-  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization along with cross-validation, and computing accuracy and Macro F1 scores.
+  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores.
 The results showed that the Neural Network model
   acheived the highest accuracy of $80\%$ and Macro F1 score of BLANK. %%TODO fill in the score.%%
-  These scores show the model's ability to accurately classify the selected websites based on captured network packet data.
+  These scores display the model's ability to accurately classify the selected websites based on captured network packet data.
 

### 2024-05-02 Final_Report/paper.tex
Added in subsubsections to section 2
Touch ups

@@
 \subsection{Capturing Data}
+\subsubsection{Wireshark}
+\subsubsection{Data Collection}
+
 \subsection{Data Preparation and Processing}
+
+\subsubsection{Feature Selection}
+\subsubsection{Data Formatting}
+
 \subsection{Employed models}
+\subsubsection{Logistic Regression (Baseline)}
+
+\subsubsection{K-Nearest Neighbors}
+
+\subsubsection{Random Forest}
+
+\subsubsection{Neural Network}
 \section{Evaluation}
@@
 \subsection{Dataset}
-\subsection{Model Evaluation}
+\subsection{Evaluation Metrics}
+Accuracy and Macro F1 score are the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
+a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
 \subsection{Model Comparison and Evaluation Results}

### 2024-05-02 GraphModels.py
Added graphs

@@ -1,0 +1,90 @@
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from sklearn import metrics
+from mpl_toolkits import mplot3d
+import seaborn as sns
+import matplotlib.patches as mpatches
+import matplotlib.ticker as mticker
+
+
+
+class Graphs:
+    def __init__(self, dataset,actual,predicted):
+        self.dataset = dataset
+        self.actual = actual
+        self.predicted = predicted
+  
+    #test the data and get the accuracy 
+    import matplotlib.patches as mpatches
+
+    def scatterPlot(self, title):
+        z = self.dataset["Protocol"]
+        x = self.dataset["Length"]
+        y = self.dataset["Time"]
+        websitesActual = self.actual
+        websitesPredicted = self.predicted
+        color_map = {'Linkedin': 'red', 'Blackboard': 'blue', 'ChatGPT': 'green'}
+
+        # --- Create actual classified packets plot ---
+        figActual = plt.figure(figsize=(16, 9))
+        ax = plt.axes(projection="3d")
+
+        # Add x, y gridlines
+        ax.grid(b=True, color='grey', linestyle='-.', linewidth=0.3, alpha=0.2)
+
+        # Create colors based on website
+        colors = [color_map.get(name, 'gray') for name in websitesActual]
+
+        # Create scatter plot
+        ax.scatter3D(x, y, z, c=colors, marker='o')
+
+        plt.title("Actual Classified Packets")
+        ax.set_xlabel('Length Of Packet', fontweight='bold')
+        ax.set_ylabel('Packet Transmission Time', fontweight='bold')
+        ax.set_zlabel('Protocol Type', fontweight='bold')
+
+        # --- Create legend for actual classified packets ---
+        handles = [mpatches.Patch(color=color_map[website]) for website in color_map]
+        labels = color_map.keys()
+        ax.legend(handles, labels, title="Website")  # Add legend to the actual plot
+
+        # --- Create predicted packets plot ---
+        figPredicted = plt.figure(figsize=(16, 9))
+        ax = plt.axes(projection="3d")
+
+        # Add x, y gridlines
+        ax.grid(b=True, color='grey', linestyle='-.', linewidth=0.3, alpha=0.2)
+
+        colors = [color_map.get(name, 'gray') for name in websitesPredicted]
+
+        # Create scatter plot  
[…]

### 2024-05-02 KNN.py

@@ -10,6 +10,11 @@ from sklearn.model_selection import KFold, LeaveOneOut
 from sklearn.metrics import confusion_matrix, classification_report, ConfusionMatrixDisplay
 from sklearn.utils import resample
 
+import GraphModels
+
+
+
+
 protocolMap = {}
 # infoMap = {}
 
@@ -32,7 +37,6 @@ def qualifier(model, X, y):
 
 def reformatInfoAndPacket(dataframe):
     protocols = dataframe["Protocol"].value_counts().index
-    infos = dataframe["Info"].value_counts().index
     
     for protocol in protocols:
         if protocol not in protocolMap.keys():
@@ -76,23 +80,23 @@ def convertWireSharkData(chatGPTcsv,blackboardcsv, linkedIncsv, sizeOfDataFrame 
 
 def trainData():
     data = convertWireSharkData("lakeData/train/chatdata.csv","lakeData/train/blackboardData.csv","lakeData/train/linkedindata.csv",7000 )
-    print(f"Train data contains {len(data)} packets")
+    # print(f"Train data contains {len(data)} packets")
     X = data.drop(columns="Website").values
     y = data["Website"].astype("category").values
-    K_range = np.linspace(10,30).astype('int64')
-    K_range
-    internalValiation = []
-    externalValidation = []
+    # K_range = np.linspace(10,30).astype('int64')
+    # K_range
+    # internalValiation = []
+    # externalValidation = []
 
-    for k in K_range:
+    # for k in K_range:
 
-        model = KNeighborsClassifier(n_neighbors=k, weights="distance")
-        # we need internalTemp and externalTemp values because you dont want to call the qualifier twice which would waste more time and memory
-        internalTemp, externalTemp = qualifier(model,X,y)
-        internalValiation.append(internalTemp)
-        externalValidation.append(externalTemp)
-    print(f" the K range with the highest accuracy {K_range[np.argmax(externalValidation)]}, with an accuracy of: {max(externalValidation)}")
-    highestAccuracyK = K_range[np.argmax(externalValidation)]
+    #     model = KNeighborsClassifier(n_neighbors=k, weights="distance")
+    #     # we need internalTemp and externalTemp values because you dont want to call the qualifier twice which would waste more time and memory
+    #     internalTemp, externalTemp = qualifier(model,X,y)
[…]

### 2024-05-02 LogReg.py

@@ -12,6 +12,7 @@ from sklearn.utils import resample
 from sklearn.model_selection import train_test_split as tts
 
 
+
 protocolMap = {}
 
 def compare_classes(actual, predicted, names=None):

### 2024-05-02 Final_Report/paper.tex
data collection started

@@
 \subsubsection{Wireshark}
+
 \subsubsection{Data Collection}
+To commence the collection of our data, we open Wireshark and select a network connection. 
+In this project we established a connection the College of William and Mary's network interface (en0). In order to isolate the web traffic in order to specifically collect 
+packets that we are analyzing, the capture filter functionality is utilized.
+The website of interest is then visited in the web browser which causes Wireshark to begin collecting the packets being exchanged.
+After collecting sufficient packets, the data is then converted into a Comma Seperated Values (CSV).
+This process of data collection is performed for Blackboard, LinkedIn, and ChatGPT resulting in the creation of
+three distinct files.
 

### 2024-05-02 Final_Report/paper.tex
Wireshark reference added
Added in equations for Acc, MF1, Recall, and precision

@@
 \documentclass[10pt,sigconf,letterpaper,nonacm]{acmart}
+
+\DeclareMathSizes{12}{30}{16}{12}
 
@@
 \subsection{Evaluation Metrics}
-Accuracy and Macro F1 score are the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
+Accuracy and Macro F1 score were the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
 a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
+\newline \\
+The equation for \textbf{Accuracy}: \\
+\[
+Accuracy= \frac{TP + TN}{TS}
+\]
+\newline \\
+The equation for \textbf{Macro F1}: \\
+\[
+Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision*Recall}{Precision_i+Recall_i}
+\]
+\newline \\
+The equation for \textbf{Recall}: \\
+\[
+Recall= \frac{TP}{TP + FN}
+\]
+\newline \\
+The equation for \textbf{Precision}: \\
+\[
+Accuracy= \frac{TP}{TP + FP}
+\]
+Accuracy is the score that rates the effectivness of a model at classification overall (ie. how many it predicited correctly out of the total set).
+
+Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores accross all classes.
+
+Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
+Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
+
 \subsection{Model Comparison and Evaluation Results}
@@
 \cite{scikit-learn}
+\cite{Wireshark}
 

### 2024-05-02 RF.py
Added new RF code

@@ -9,6 +9,7 @@ from sklearn.tree import DecisionTreeClassifier as DTC
 from sklearn import tree
 from sklearn.ensemble import RandomForestClassifier as RFC
 from sklearn.utils import resample
+import GraphModels
 
 
 protocolMap = {}
@@ -142,9 +143,9 @@ def convertWMdata(wmCSV):
 
 #Repalce with actual data 
 #TODO
-chatGPTcsv = "lakeData/train/4-8_chatGPT.csv"
-blackboardcsv = "lakeData/train/4-9_blackboard.csv"
-linkedIncsv = "lakeData/train/4-9_linkedin.csv"
+chatGPTcsv = "lakeData/train/chatdata.csv"
+blackboardcsv = "lakeData/train/blackboardData.csv"
+linkedIncsv = "lakeData/train/linkedindata.csv"
 
 data = convertWireSharkData(chatGPTcsv,blackboardcsv,linkedIncsv)
 
@@ -185,30 +186,35 @@ results.head()
 
 print(results[results['rank_test_score'] == 1])
 
-rfc_final = RFC(n_estimators=100, max_depth=9, min_samples_split=5, random_state=201)
-rfc_final.fit(Xtrain, ytrain)
+rfc_final = RFC(n_estimators=100, max_depth=13, min_samples_split=5, random_state=201)
+rfc_final.fit(X, y)
 print('Train Score: ', rfc_final.score(Xtrain, ytrain))
 print('Test Score: ', rfc_final.score(Xtest, ytest))
 
 #Confusion matrix 
-y_names = ["ChatGPT","Blackboard","LinkedIn"]
-cnf_matrix, accuracy = compare_classes(ytest, rfc_final.predict(Xtest), y_names)
-print(cnf_matrix, accuracy)
+#y_names = ["Blackboard","ChatGPT","LinkedIn"]
+#graph = GraphModels.Graphs(Xtest, ytest, rfc_final.predict(Xtest))
+#print(Xtest)
+#graph.confusionMatrix("Random Forest Confusion Matrix"), graph.scatterPlot("Random Forest Scatter Plot")
+#cnf_matrix, accuracy = compare_classes(ytest, rfc_final.predict(Xtest), y_names)
+#print(cnf_matrix, accuracy)
 
 #Make heatmap visual 
-sns.heatmap(cnf_matrix, cmap='Purples', vmin=0, vmax=800,
-            annot=True, fmt='.2f', xticklabels=y_names, yticklabels=y_names)
[…]

### 2024-05-02 Final_Report/paper.tex
Fixed equation error
edited paper
added data collection subsection

@@
 \subsubsection{Data Collection}
-To commence the collection of our data, we open Wireshark and select a network connection. 
-In this project we established a connection the College of William and Mary's network interface (en0). In order to isolate the web traffic in order to specifically collect 
-packets that we are analyzing, the capture filter functionality is utilized.
-The website of interest is then visited in the web browser which causes Wireshark to begin collecting the packets being exchanged.
-After collecting sufficient packets, the data is then converted into a Comma Seperated Values (CSV).
-This process of data collection is performed for Blackboard, LinkedIn, and ChatGPT resulting in the creation of
-three distinct files.
+To maintain normalized representation in all the collected datasets, a process of data harmonization 
+was applied after collecting the necessary data. The dataset with the minimum number of observations is identified and accounted for when
+truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
+This process ensures a balanced yet unbaised dataset that maximizes the effectivness of our models.
 
 \subsection{Data Preparation and Processing}
+After collecting the necessary data,
 
 \subsubsection{Feature Selection}
+
 \subsubsection{Data Formatting}
@@
 \[
-Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision*Recall}{Precision_i+Recall_i}
+Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
 \]

### 2024-05-02 Final_Report/paper.tex
added data colection

--- 2024-05-02 Final_Report/paper.tex
@@
 \subsection{Data Preparation and Processing}
+To maintain normalized representation in all the collected datasets, a process of data harmonization 
+was applied after collecting the necessary data. The dataset with the minimum number of observations is identified and accounted for when
+truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
+This process ensures a balanced yet unbaised dataset that maximizes the effectivness of our models.
 
 \subsubsection{Feature Selection}
+
 \subsubsection{Data Formatting}

### 2024-05-03 NN.py
ran bigger gridsearch on lab machine

@@ -3,7 +3,7 @@ import pandas as pd
 import matplotlib.pyplot as plt
 from sklearn.model_selection import GridSearchCV
 from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score, confusion_matrix, ConfusionMatrixDisplay
+from sklearn.metrics import accuracy_score, confusion_matrix
 from sklearn.neural_network import MLPClassifier
 from sklearn.preprocessing import StandardScaler
 from sklearn.utils import resample
@@ -38,20 +38,20 @@ def grid_search(X, y):
     mlp = MLPClassifier(random_state=RAND_ST, max_iter=1000)
 
     # real params for initial large gridsearch
-    # parameters = {
-    #     'activation': ['identity', 'logistic', 'tanh', 'relu'],
-    #     'solver': ['adam','lbfgs','sgd'],
-    #     'alpha': 10.0 ** -np.arange(-1, 10),
-    #     'hidden_layer_sizes':[[i for i in range(4,10)] for j in range(4,10)]
-    # }
+    parameters = {
+        'activation': ['identity', 'logistic', 'tanh', 'relu'],
+        'solver': ['adam','lbfgs','sgd'],
+        'alpha': 10.0 ** -np.arange(-1, 10),
+        'hidden_layer_sizes':[[i for i in range(4,10)] for j in range(4,10)]
+    }
 
     # test params for debug
-    parameters = {
-        'activation': ['relu'],
-        'solver': ['adam','lbfgs'],
-        'alpha': [0.0001],
-        'hidden_layer_sizes':(9,),
-    }
+    # parameters = {
+    #     'activation': ['relu'],
+    #     'solver': ['adam','lbfgs'],
+    #     'alpha': [0.0001],
+    #     'hidden_layer_sizes':(9,),
+    # }
 
     gs = GridSearchCV(mlp, parameters, n_jobs=-1, scoring="accuracy", verbose=3)
     gs.fit(X, y)

### 2024-05-03 NN.py
fixed hidden_layer_sizes mistake I think

@@ -42,8 +42,10 @@ def grid_search(X, y):
         'activation': ['identity', 'logistic', 'tanh', 'relu'],
         'solver': ['adam','lbfgs','sgd'],
         'alpha': 10.0 ** -np.arange(-1, 10),
-        'hidden_layer_sizes':[[i for i in range(4,10)] for j in range(4,10)]
+        'hidden_layer_sizes':[[0],[1],[2],[3],[4],[5],[6],[7],[8],[9],[10]]
+        # only testing single layer
     }
+
 
     # test params for debug
     # parameters = {

### 2024-05-03 NN.py
fixed node list errors, trying one hidden layer only now

@@ -42,8 +42,9 @@ def grid_search(X, y):
         'activation': ['identity', 'logistic', 'tanh', 'relu'],
         'solver': ['adam','lbfgs','sgd'],
         'alpha': 10.0 ** -np.arange(-1, 10),
-        'hidden_layer_sizes':[[0],[1],[2],[3],[4],[5],[6],[7],[8],[9],[10]]
+        'hidden_layer_sizes':[(3),(4),(5),(6),(7),(8),(9),(10),(11),(12)]
         # only testing single layer
+        # smallest must be 3 or error, since there are 3 output nodes
     }
 
 

### 2024-05-03 NN.py
test ran, 12 most successful, so running again

@@ -42,7 +42,7 @@ def grid_search(X, y):
         'activation': ['identity', 'logistic', 'tanh', 'relu'],
         'solver': ['adam','lbfgs','sgd'],
         'alpha': 10.0 ** -np.arange(-1, 10),
-        'hidden_layer_sizes':[(3),(4),(5),(6),(7),(8),(9),(10),(11),(12)]
+        'hidden_layer_sizes':[(12),(13),(14),(15),(16),(17),(18),(19),(20),]
         # only testing single layer
         # smallest must be 3 or error, since there are 3 output nodes
     }

### 2024-05-03 main.py

@@ -66,8 +66,8 @@ def main():
     # Use the same test data for all models
     test_data = get_data("Test")
 
-    knn_train_data = get_data("Train", KNN_TRAIN_SIZE)
-    run_KNN(knn_train_data, test_data)
+    # knn_train_data = get_data("Train", KNN_TRAIN_SIZE)
+    # run_KNN(knn_train_data, test_data)
 
     nn_train_data = get_data("Train")
     run_NN(nn_train_data, test_data)

### 2024-05-04 NN.py
finished 12-20 gridsearch

@@ -42,7 +42,7 @@ def grid_search(X, y):
         'activation': ['identity', 'logistic', 'tanh', 'relu'],
         'solver': ['adam','lbfgs','sgd'],
         'alpha': 10.0 ** -np.arange(-1, 10),
-        'hidden_layer_sizes':[(12),(13),(14),(15),(16),(17),(18),(19),(20),]
+        'hidden_layer_sizes':[(20),(25),(30),(35),(40),(45),(50),(55),(60),(65),(70)]
         # only testing single layer
         # smallest must be 3 or error, since there are 3 output nodes
     }

### 2024-05-04 NN.py
grid search results inputted

@@ -10,6 +10,7 @@ from sklearn.utils import resample
 from seaborn import heatmap
 
 from utils import RAND_ST, compare_classes
+MAX_ITER = 1000
 
 
 def pre_process(train_data, test_data):
@@ -35,7 +36,7 @@ def pre_process(train_data, test_data):
 
 
 def grid_search(X, y):
-    mlp = MLPClassifier(random_state=RAND_ST, max_iter=1000)
+    mlp = MLPClassifier(random_state=RAND_ST, max_iter=MAX_ITER)
 
     # real params for initial large gridsearch
     parameters = {
@@ -74,8 +75,22 @@ def grid_search(X, y):
     return gs
 
 
-def predict_and_show(gs, X_test, y_test):
-    test_pred = gs.predict(X_test)
+def make_nn(X, y, X_test, y_test):
+    # values obtained from gridsearch
+    mlp = MLPClassifier(
+        activation="logistic",
+        solver="lbfgs",
+        alpha=0.1,
+        hidden_layer_sizes=(60),
+        random_state=RAND_ST,
+        max_iter=MAX_ITER
+    )
+    mlp.fit(X,y)
+    return mlp
+
+
+def predict_and_show(model, X_test, y_test):
+    test_pred = model.predict(X_test)
     test_score = accuracy_score(test_pred, y_test)
     print("score on test data: ",test_score)
 
@@ -94,6 +109,7 @@ def run_NN(train_data, test_data):
     print("Starting Neural Network")
 
     X, y, X_test, y_test = pre_process(train_data, test_data)
-    gs = grid_search(X, y)
-    predict_and_show(gs, X_test, y_test)
+    # model = grid_search(X, y)
+    model = make_nn(X, y, X_test, y_test)
+    predict_and_show(model, X_test, y_test)
 

### 2024-05-04 main.py

@@ -43,8 +43,8 @@ def csv_dir_to_df(dir_path):
 
 
 def get_data(dataset, size=0):
-    chatgpt_df      = csv_dir_to_df("Data/" + dataset + "/LinkedIn")
-    linkedin_df     = csv_dir_to_df("Data/" + dataset + "/ChatGPT")
+    chatgpt_df      = csv_dir_to_df("Data/" + dataset + "/ChatGPT")
+    linkedin_df     = csv_dir_to_df("Data/" + dataset + "/LinkedIn")
     blackboard_df   = csv_dir_to_df("Data/" + dataset + "/Blackboard")
     
     sampleSize = min(len(chatgpt_df), len(blackboard_df), len(linkedin_df))
@@ -53,8 +53,8 @@ def get_data(dataset, size=0):
     linkedin_df     = resample(linkedin_df, replace=False, n_samples=sampleSize, random_state=RAND_ST)
     blackboard_df   = resample(blackboard_df, replace=False, n_samples=sampleSize, random_state=RAND_ST)
 
-    linkedin_df["Website"] = "LinkedIn"
     chatgpt_df["Website"] = "ChatGPT"
+    linkedin_df["Website"] = "LinkedIn"
     blackboard_df["Website"] = "Blackboard"
 
     combined = pd.concat([chatgpt_df, linkedin_df, blackboard_df])

### 2024-05-04 GraphModels.py
ugh not working

@@ -1,0 +1,86 @@
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from sklearn import metrics
+from mpl_toolkits import mplot3d
+import seaborn as sns
+import matplotlib.patches as mpatches
+import matplotlib.ticker as mticker
+
+
+
+class Graphs:
+    def __init__(self, dataset,actual,predicted):
+        self.dataset = dataset
+        self.actual = actual
+        self.predicted = predicted
+  
+    #test the data and get the accuracy 
+    import matplotlib.patches as mpatches
+
+    def scatterPlot(self, title):
+        z = self.dataset["Protocol"]
+        x = self.dataset["Length"]
+        y = self.dataset["Time"]
+        websitesActual = self.actual
+        websitesPredicted = self.predicted
+        color_map = {'Linkedin': 'red', 'Blackboard': 'blue', 'ChatGPT': 'green'}
+
+        # --- Create actual classified packets plot ---
+        figActual = plt.figure(figsize=(16, 9))
+        ax = plt.axes(projection="3d")
+
+        # Add x, y gridlines
+        ax.grid(b=True, color='grey', linestyle='-.', linewidth=0.3, alpha=0.2)
+
+        # Create colors based on website
+        colors = [color_map.get(name, 'gray') for name in websitesActual]
+
+        # Create scatter plot
+        ax.scatter3D(x, y, z, c=colors, marker='o')
+
+        plt.title("Actual Classified Packets")
+        ax.set_xlabel('Length Of Packet', fontweight='bold')
+        ax.set_ylabel('Packet Transmission Time', fontweight='bold')
+        ax.set_zlabel('Protocol Type', fontweight='bold')
+
+        # --- Create legend for actual classified packets ---
+        handles = [mpatches.Patch(color=color_map[website]) for website in color_map]
+        labels = color_map.keys()
+        ax.legend(handles, labels, title="Website")  # Add legend to the actual plot
+
+        # --- Create predicted packets plot ---
+        figPredicted = plt.figure(figsize=(16, 9))
+        ax = plt.axes(projection="3d")
+
+        # Add x, y gridlines
+        ax.grid(b=True, color='grey', linestyle='-.', linewidth=0.3, alpha=0.2)
+
+        colors = [color_map.get(name, 'gray') for name in websitesPredicted]
+
+        # Create scatter plot  
+        ax.scatter3D(x, y, z, c=colors, marker='o')
+
[…]

### 2024-05-04 NN.py

@@ -10,7 +10,9 @@ from sklearn.utils import resample
 from seaborn import heatmap
 
 from utils import RAND_ST, compare_classes
-MAX_ITER = 1000
+import GraphModels
+
+MAX_ITER = 2000
 
 
 def pre_process(train_data, test_data):
@@ -91,17 +93,7 @@ def make_nn(X, y, X_test, y_test):
 
 def predict_and_show(model, X_test, y_test):
     test_pred = model.predict(X_test)
-    test_score = accuracy_score(test_pred, y_test)
-    print("score on test data: ",test_score)
-
-    y_names = ["ChatGPT","Blackboard","LinkedIn"]
-    confusion_matrix, accuracy = compare_classes(y_test, test_pred, y_names)
-    print(confusion_matrix)
-
-    heatmap(confusion_matrix, cmap='Purples',
-            vmin=0, vmax=800,
-            annot=True, fmt='.2f',
-            xticklabels=y_names, yticklabels=y_names)
+    graph = GraphModels.Graphs(X_test, y_test, test_pred)
     plt.show()
 
 

### 2024-05-04 NN.py
testing the outputting of the Conf Matrix

@@ -41,29 +41,31 @@ def grid_search(X, y):
     mlp = MLPClassifier(random_state=RAND_ST, max_iter=MAX_ITER)
 
     # real params for initial large gridsearch
-    parameters = {
-        'activation': ['identity', 'logistic', 'tanh', 'relu'],
-        'solver': ['adam','lbfgs','sgd'],
-        'alpha': 10.0 ** -np.arange(-1, 10),
-        'hidden_layer_sizes':[(20),(25),(30),(35),(40),(45),(50),(55),(60),(65),(70)]
+    # parameters = {
+    #     'activation': ['identity', 'logistic', 'tanh', 'relu'],
+    #     'solver': ['adam','lbfgs','sgd'],
+    #     'alpha': 10.0 ** -np.arange(-1, 10),
+    #     'hidden_layer_sizes':[(20),(20,20),(30),(30,30),(40),(40,40),(50),(50,50),(60),(60,60)]
         # only testing single layer
         # smallest must be 3 or error, since there are 3 output nodes
-    }
+    # }
 
 
     # test params for debug
-    # parameters = {
-    #     'activation': ['relu'],
-    #     'solver': ['adam','lbfgs'],
-    #     'alpha': [0.0001],
-    #     'hidden_layer_sizes':(9,),
-    # }
+    parameters = {
+        'activation': ['relu'],
+        'solver': ['adam','lbfgs'],
+        'alpha': [0.0001],
+        'hidden_layer_sizes':(9,),
+    }
 
-    gs = GridSearchCV(mlp, parameters, n_jobs=-1, scoring="accuracy", verbose=3)
+    gs = GridSearchCV(mlp, parameters, n_jobs=-1, scoring="accuracy")
     gs.fit(X, y)
 
     # Store and print data for analysis
+    print("Best score:")
     print(gs.score(X, y))
+    print("Best params:")
     print(gs.best_params_)
     results = pd.DataFrame(gs.cv_results_)
     results = results[['param_activation','param_solver',
@@ -94,6 +96,8 @@ def make_nn(X, y, X_test, y_test):
 def predict_and_show(model, X_test, y_test):
     test_pred = model.predict(X_test)
     graph = GraphModels.Graphs(X_test, y_test, test_pred)
+    graph.confusionMatrix("NN Confusion Matrix")
+    plt.savefig("Figures_and_Graphs/ConfusionMatrixNN.png")
     plt.show()
 
 
[…]

### 2024-05-04 GraphModels.py
Added Graphs

@@ -83,7 +83,7 @@ class Graphs:
         ax.xaxis.set_ticklabels(np.unique(self.predicted)); ax.yaxis.set_ticklabels(np.unique(self.predicted))
         return 
 
-
+  
 
 
 

### 2024-05-04 KNN.py

@@ -73,7 +73,7 @@ def convertWireSharkData(chatGPTcsv,blackboardcsv, linkedIncsv, sizeOfDataFrame 
     if sizeOfDataFrame == 0:
         sizeOfDataFrame = len(numericData)
     downSampledData = resample(numericData,replace=False, n_samples=sizeOfDataFrame,random_state=42)
-    #print(downSampledData)
+    print(downSampledData)
     return downSampledData
 
 

### 2024-05-04 NN.py
should work now I hope

@@ -81,15 +81,24 @@ def grid_search(X, y):
 
 def make_nn(X, y, X_test, y_test):
     # values obtained from gridsearch
+    # mlp = MLPClassifier(
+    #     activation="logistic",
+    #     solver="lbfgs",
+    #     alpha=0.1,
+    #     hidden_layer_sizes=(60),
+    #     random_state=RAND_ST,
+    #     max_iter=MAX_ITER
+    # )
     mlp = MLPClassifier(
-        activation="logistic",
-        solver="lbfgs",
-        alpha=0.1,
-        hidden_layer_sizes=(60),
+        activation="relu",
+        solver="adam",
+        alpha=0.0001,
+        hidden_layer_sizes=(9),
         random_state=RAND_ST,
         max_iter=MAX_ITER
     )
     mlp.fit(X,y)
+    mlp.score(X, y)
     return mlp
 
 
@@ -105,7 +114,7 @@ def run_NN(train_data, test_data):
     print("Starting Neural Network")
 
     X, y, X_test, y_test = pre_process(train_data, test_data)
-    model = grid_search(X, y)
-    # model = make_nn(X, y, X_test, y_test)
+    # model = grid_search(X, y)
+    model = make_nn(X, y, X_test, y_test)
     predict_and_show(model, X_test, y_test)
 

### 2024-05-04 Final_Report/paper.tex
added data preparation and processing

@@
 \subsection{Data Preparation and Processing}
+In order to ensure the integrity and reliability of our models,
+the collected data must be processed prior to model training.
+
+\subsubsection{Feature Selection}
+
+\subsubsection{Data Formatting}
 To maintain normalized representation in all the collected datasets, a process of data harmonization 
@@
 This process ensures a balanced yet unbaised dataset that maximizes the effectivness of our models.
-
-\subsubsection{Feature Selection}
-
-\subsubsection{Data Formatting}
 

### 2024-05-04 Final_Report/paper.tex
Added in intro to section 2.3 and random forest section (still need a figure for it)

--- 2024-05-02 Final_Report/paper.tex
@@
 % \usepackage{color}
-% \usepackage{graphicx}
+\usepackage{graphicx}
 % \usepackage[labelformat=simple]{subcaption}
@@
 \subsection{Capturing Data}
-\subsubsection{Wireshark}
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=\textwidth]{Figures_and_Graphs/webCollectionDiagram.png}
+  \caption{Wireshark Data Collection Process}
+  \label{fig:dataCollection}
+\end{figure*}
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/wiresharkFigure.png}
+  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/wiresharkDataFigure.png}
+  \caption{Wireshark interface and example of captured data}
+  \label{fig:wireshark}
+\end{figure*}
+\subsubsection{Network analysis tool} For this project, the tool chosen and used was Wireshark \cite{Wireshark}, a widely used network protocol analyzer.
+Wireshark is capable of capturing and analyzing network packets, and is able to provide a detailed
+ view of the packets exchanged between the client and server.
+Wireshark offers a broad variety of features that allow for users to capture, decode, and analyze network packets.
+It shows the packet data in a human-readable format, and provides a detailed view of the packet's contents.
+ This data contains information on time taken for packet to send and arrive, protocols used, size of each packet, and other fields such as more information on the packet and the source IP address.
+This tool also supports use of different forms of link communication and can be specified to capture packets from a specific network interface (ie.
+Ethernet, Wifi, etc.).
+ The many applications and ease of use of Wireshark make it a great tool for this project.
+
+ The process for this project (shown in Figure 1) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
 
@@
 The website of interest is then visited in the web browser which causes Wireshark to begin collecting the packets being exchanged.
-After collecting sufficient packets, the data is then converted into a Comma Seperated Values (CSV).
+After collecting sufficient packets, the data is then converted into a Comma Separated Values (CSV).
 This process of data collection is performed for Blackboard, LinkedIn, and ChatGPT resulting in the creation of
@@
 truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
-This process ensures a balanced yet unbaised dataset that maximizes the effectivness of our models.
+This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models.
 
@@
 \subsection{Employed models}
+For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet.
+We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network.
+The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution.
+These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet.
+We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
 \subsubsection{Logistic Regression (Baseline)}
@@
 \subsubsection{Random Forest}
+A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
+Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees.
+
+Advantages of Random Forest Models:
+\begin{enumerate}
+  \item \textbf{Ability to handle complex features}: Random forests have the ability to handle complex features, such as time and protocols in the case of network packets, and the relationships between them, which can be very important in classifying network traffic.
+  \item \textbf{High accuracy}: Random forests diminishes the problem of overfitting that can occur in decision trees, and can achieve higher accuracy, helping to more accurately determine website origins of a packet.
+  \item \textbf{Feature importance}: Random forests can provide insight into which features are most important in the classification process, such as protocol vs time in classifying websites for this project.
+  \item \textbf{Scalability}: Random forests can be scaled to handle much larger datasets, which can be very important for network traffic which can receive a high volume of packet data extremely quick.
+\end{enumerate}
+
+The library used for the Random Forest model was scikit-learn \cite{scikit-learn}.
+Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
+Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
 
@@
 \]
-Accuracy is the score that rates the effectivness of a model at classification overall (ie. how many it predicited correctly out of the total set).
+\\
+Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
 
-Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores accross all classes.
+Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.
 
-Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
-Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
+Recall is the calculation of how many classifications the model got correct (ie. how many truly belong in that class in the entire dataset). 
+Precision is the calculation of how many classifications truly belong to each class (ie. can be thought of as class accuracy).
 

### 2024-05-04 LogReg.py
adjusted LogReg cfile to include GraphModels class

@@ -11,6 +11,8 @@ from sklearn.metrics import confusion_matrix, classification_report
 from sklearn.utils import resample
 from sklearn.model_selection import train_test_split as tts
 
+import GraphModels
+
 
 
 protocolMap = {}
@@ -88,7 +90,29 @@ data = convertWireSharkData(chatGPTcsv,blackboardcsv,linkedIncsv )
 
 
 
+def trainData():
+    data = convertWireSharkData("lakeData/train/chatdata.csv","lakeData/train/blackboardData.csv","lakeData/train/linkedindata.csv",7000 )
+    # print(f"Train data contains {len(data)} packets")
+    X = data.drop(columns="Website").values
+    y = data["Website"].astype("category").values
+    # K_range = np.linspace(10,30).astype('int64')
+    # K_range
+    # internalValiation = []
+    # externalValidation = []
 
+    # for k in K_range:
+
+    #     model = KNeighborsClassifier(n_neighbors=k, weights="distance")
+    #     # we need internalTemp and externalTemp values because you dont want to call the qualifier twice which would waste more time and memory
+    #     internalTemp, externalTemp = qualifier(model,X,y)
+    #     internalValiation.append(internalTemp)
+    #     externalValidation.append(externalTemp)
+    print(f" the K range with the highest accuracy {12}, with an accuracy of: {97}%")
+    highestAccuracyK = 12
+    model = KNeighborsClassifier(n_neighbors=highestAccuracyK, weights="distance")
+    model.fit(X, y)
+    print(model.score(X,y))
+    return model
 
 
 X_df = data.drop(columns="Website").values
@@ -112,3 +136,20 @@ confusionMatrix, accuracy = compare_classes(actualClasses,predictedClasses)
 print(confusionMatrix,accuracy)
 
 
+def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
+    testData = convertWireSharkData(testDataChatgpt,testDataBlackboard,testDataLinkedIn)
+    actualClasses = testData["Website"]
+    testData = testData.drop("Website", axis = 1)
+    predictedClasses = model.predict(testData)
+
+    graph = GraphModels.Graphs(testData,actualClasses,predictedClasses)
+    
+    
+
+
+    return graph.confusionMatrix("LogReg Confusion Matrix"), graph.scatterPlot("Logistic Regression")
+
+model = trainData()
[…]

### 2024-05-04 Final_Report/paper.tex
Added RF figure as example of structure

@@
 A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
-Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees.
+Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure 3).
 
@@
 Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=9cm]{Figures_and_Graphs/RandomForestExample.png}
+  \caption{Random Forest model structure example}
+  \label{fig:RFExample}
+\end{figure}
 

### 2024-05-04 Final_Report/paper.tex
updated LogReg file and began writing Logistic Reg

--- 2024-05-04 Final_Report/paper.tex
@@
 \subsection{Employed models}
-For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet.
-We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network.
-The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution.
-These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet.
-We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
 \subsubsection{Logistic Regression (Baseline)}
+As a starting point, we employed the Logistic Regression model as a baseline for our data analysis.
+Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
+It was understoof initiallly that this model may not be an ideal fit for our data, due to the regressions binary nature having more than two classifications is not ideal.
+However, for our purposes this was an excellent baseline.
+It was important for us to first visualize what features define network traffic so that we could further model around them, and the logistic regression was the most efficient choice for that.
+Our model returned us an accuracy score of .56, or 56\%, which is less than ideal but not entirely unexpected.
+To analyze the data further, we put the results from our model into a confusion matrix.
+With this we were able to see that the model predicted Blackboard quite well, atleast in comparison to ChatGPT and Linkedin which were far poorer.
 
@@
 \subsubsection{Random Forest}
-A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
-Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees.
-
-Advantages of Random Forest Models:
-\begin{enumerate}
-  \item \textbf{Ability to handle complex features}: Random forests have the ability to handle complex features, such as time and protocols in the case of network packets, and the relationships between them, which can be very important in classifying network traffic.
-  \item \textbf{High accuracy}: Random forests diminishes the problem of overfitting that can occur in decision trees, and can achieve higher accuracy, helping to more accurately determine website origins of a packet.
-  \item \textbf{Feature importance}: Random forests can provide insight into which features are most important in the classification process, such as protocol vs time in classifying websites for this project.
-  \item \textbf{Scalability}: Random forests can be scaled to handle much larger datasets, which can be very important for network traffic which can receive a high volume of packet data extremely quick.
-\end{enumerate}
-
-The library used for the Random Forest model was scikit-learn \cite{scikit-learn}.
-Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
-Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
 
@@
 \]
-\\
 Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
@@
 
-Recall is the calculation of how many classifications the model got correct (ie. how many truly belong in that class in the entire dataset). 
-Precision is the calculation of how many classifications truly belong to each class (ie. can be thought of as class accuracy).
+Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
+Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
 

### 2024-05-04 LogReg.py

@@ -39,6 +39,8 @@ def compare_classes(actual, predicted, names=None):
     
     print('Accuracy = ' + format(accuracy, '.2f'))
     return conf_mat, accuracy
+
+
 def reformatInfoAndPacket(dataframe):
     protocols = dataframe["Protocol"].value_counts().index
 
@@ -52,6 +54,7 @@ def reformatInfoAndPacket(dataframe):
         return dataframe[["Time", "Protocol", "Length","Website"]]
     else:
         return dataframe[["Time", "Protocol", "Length"]]
+    
 
 def convertWireSharkData(chatGPTcsv,blackboardcsv, linkedIncsv, sizeOfDataFrame = 0):
     chatGPT = pd.read_csv(chatGPTcsv)
@@ -86,54 +89,20 @@ chatGPTcsv = "lakeData/train/4-8_chatGPT.csv"
 blackboardcsv = "lakeData/train/4-9_blackboard.csv"
 linkedIncsv = "lakeData/train/4-9_linkedin.csv"
 
-data = convertWireSharkData(chatGPTcsv,blackboardcsv,linkedIncsv )
-
-
 
 def trainData():
-    data = convertWireSharkData("lakeData/train/chatdata.csv","lakeData/train/blackboardData.csv","lakeData/train/linkedindata.csv",7000 )
-    # print(f"Train data contains {len(data)} packets")
-    X = data.drop(columns="Website").values
+    data = convertWireSharkData(chatGPTcsv,blackboardcsv,linkedIncsv )
+    X_df = data.drop(columns="Website").values
+    X = np.array(X_df)
     y = data["Website"].astype("category").values
-    # K_range = np.linspace(10,30).astype('int64')
-    # K_range
-    # internalValiation = []
-    # externalValidation = []
-
-    # for k in K_range:
-
-    #     model = KNeighborsClassifier(n_neighbors=k, weights="distance")
-    #     # we need internalTemp and externalTemp values because you dont want to call the qualifier twice which would waste more time and memory
-    #     internalTemp, externalTemp = qualifier(model,X,y)
-    #     internalValiation.append(internalTemp)
-    #     externalValidation.append(externalTemp)
-    print(f" the K range with the highest accuracy {12}, with an accuracy of: {97}%")
-    highestAccuracyK = 12
-    model = KNeighborsClassifier(n_neighbors=highestAccuracyK, weights="distance")
-    model.fit(X, y)
-    print(model.score(X,y))
[…]

### 2024-05-04 Final_Report/paper.tex

--- 2024-05-04 Final_Report/paper.tex
@@
 \subsubsection{Logistic Regression (Baseline)}
+As a starting point, we employed the Logistic Regression model as a baseline for our data analysis.
+Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
+It was understoof initiallly that this model may not be an ideal fit for our data, due to the regressions binary nature having more than two classifications is not ideal.
+However, for our purposes this was an excellent baseline.
+It was important for us to first visualize what features define network traffic so that we could further model around them, and the logistic regression was the most efficient choice for that.
+Our model returned us an accuracy score of .56, or 56\%, which is less than ideal but not entirely unexpected.
+To analyze the data further, we put the results from our model into a confusion matrix.
+With this we were able to see that the model predicted Blackboard quite well, atleast in comparison to ChatGPT and Linkedin which were far poorer.
 

### 2024-05-04 Final_Report/paper.tex

--- 2024-05-04 Final_Report/paper.tex
@@
 \subsection{Data Preparation and Processing}
+In order to ensure the integrity and reliability of our models,
+the collected data must be processed prior to model training.
+
+\subsubsection{Feature Selection}
+The data collection process using Wireshark yields a dataset containing seven distinct features shown in Figure 2. 
+\begin{itemize}
+  \item \textbf{Packet Number}: An integer representing the order in which the packets were captured during the Wireshark session.
+Provides insight on the order of the packets on the network interface.
+  \item \textbf{Time}: A floating point value representing the relative timestamp for each packet since the start of the Wireshark session.
+Similar to packet number, the time feature provides a better understanding of the packet order yet is more precise.
+  \item \textbf{Source}: A string value containing the internet protocol address of the device that the packet originated from. 
+  \item \textbf{Destination}: A string value containing the internet protocol address of the device that is receiving the packet. 
+  \item \textbf{Protocol}: A string value which contains the network protocol employed for the transmission of the packet.
+Three distinct protocols were identified within the datasets used in this project (QUIC, TCP and TLSv1.2).
+  \item \textbf{Length}: An integer representing the size of a packet in bits 
+  \item \textbf{Info}: A string value containing more information pertaining to a packet. This value can vary heavily between packets.
+\end{itemize} 
+As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
+Similairly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
+Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
+the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in Figure 3.
+Additionally, a categorical variable titled "Website"
+is created which displays which website the packet originated (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
+the models to detect relationships between the packets and their corresponding web traffic origin.
+
+\subsubsection{Data Formatting}
 To maintain normalized representation in all the collected datasets, a process of data harmonization 
@@
 truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
-This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models.
-
-\subsubsection{Feature Selection}
-
-\subsubsection{Data Formatting}
+This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure 3 pesents the refined data following the data preparation. 
+\begin{figure}[htp] % h: here, t: top, p: bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
+  \caption{Processed Web Traffic Data}
+  \label{fig:wireshark}
+\end{figure}
 
@@
 \subsubsection{Logistic Regression (Baseline)}
-As a starting point, we employed the Logistic Regression model as a baseline for our data analysis.
-Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
-It was understoof initiallly that this model may not be an ideal fit for our data, due to the regressions binary nature having more than two classifications is not ideal.
-However, for our purposes this was an excellent baseline.
-It was important for us to first visualize what features define network traffic so that we could further model around them, and the logistic regression was the most efficient choice for that.
-Our model returned us an accuracy score of .56, or 56\%, which is less than ideal but not entirely unexpected.
-To analyze the data further, we put the results from our model into a confusion matrix.
-With this we were able to see that the model predicted Blackboard quite well, atleast in comparison to ChatGPT and Linkedin which were far poorer.
 

### 2024-05-04 Final_Report/paper.tex
Added in dynamic ref to figures

@@
 of building models which will be able to predict the web traffic origin of a specific packet. The collection of data was performed
-using wireshark, then the data was reformatted to eliminate bias and get more accurate results.
+using Wireshark, then the data was reformatted to eliminate bias and get more accurate results.
 Using the collected data we then trained four models which had varying levels of accuracy, Logistic Regression (56\%), 
@@
 
- The process for this project (shown in Figure 1) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
+ The process for this project (shown in figure \ref{fig:dataCollection}) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
 
@@
 \subsubsection{Feature Selection}
-The data collection process using Wireshark yields a dataset containing seven distinct features shown in Figure 2. 
+The data collection process using Wireshark yields a dataset containing seven distinct features shown in figure \ref{fig:wireshark}. 
 \begin{itemize}
@@
 As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
-Similairly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
+Similarly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
 Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
-the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in Figure 3.
+the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in figure \ref{fig:webTraffic}.
 Additionally, a categorical variable titled "Website"
@@
 truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
-This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure 3 pesents the refined data following the data preparation. 
+This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure \ref{fig:webTraffic} presents the refined data following the data preparation. 
 \begin{figure}[htp] % h: here, t: top, p: bottom
@@
   \caption{Processed Web Traffic Data}
-  \label{fig:wireshark}
+  \label{fig:webTraffic}
 \end{figure}
@@
 A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
-Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure 3).
+Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure \ref{fig:RFExample}).
 

### 2024-05-04 Final_Report/paper.tex
Added to paper.tex

--- 2024-05-04 Final_Report/paper.tex
@@
 \subsection{Data Preparation and Processing}
-In order to ensure the integrity and reliability of our models,
-the collected data must be processed prior to model training.
-
-\subsubsection{Feature Selection}
-The data collection process using Wireshark yields a dataset containing seven distinct features shown in Figure 2. 
-\begin{itemize}
-  \item \textbf{Packet Number}: An integer representing the order in which the packets were captured during the Wireshark session.
-Provides insight on the order of the packets on the network interface.
-  \item \textbf{Time}: A floating point value representing the relative timestamp for each packet since the start of the Wireshark session.
-Similar to packet number, the time feature provides a better understanding of the packet order yet is more precise.
-  \item \textbf{Source}: A string value containing the internet protocol address of the device that the packet originated from. 
-  \item \textbf{Destination}: A string value containing the internet protocol address of the device that is receiving the packet. 
-  \item \textbf{Protocol}: A string value which contains the network protocol employed for the transmission of the packet.
-Three distinct protocols were identified within the datasets used in this project (QUIC, TCP and TLSv1.2).
-  \item \textbf{Length}: An integer representing the size of a packet in bits 
-  \item \textbf{Info}: A string value containing more information pertaining to a packet. This value can vary heavily between packets.
-\end{itemize} 
-As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
-Similairly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
-Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
-the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in Figure 3.
-Additionally, a categorical variable titled "Website"
-is created which displays which website the packet originated (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
-the models to detect relationships between the packets and their corresponding web traffic origin.
-
-\subsubsection{Data Formatting}
 To maintain normalized representation in all the collected datasets, a process of data harmonization 
@@
 truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
-This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure 3 pesents the refined data following the data preparation. 
-\begin{figure}[htp] % h: here, t: top, p: bottom
-  \centering
-  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
-  \caption{Processed Web Traffic Data}
-  \label{fig:wireshark}
-\end{figure}
+This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models.
+
+\subsubsection{Feature Selection}
+
+\subsubsection{Data Formatting}
 
@@
 Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
-It was understoof initiallly that this model may not be an ideal fit for our data, due to the regressions binary nature having more than two classifications is not ideal.
-However, for our purposes this was an excellent baseline.
-It was important for us to first visualize what features define network traffic so that we could further model around them, and the logistic regression was the most efficient choice for that.
-Our model returned us an accuracy score of .56, or 56\%, which is less than ideal but not entirely unexpected.
-To analyze the data further, we put the results from our model into a confusion matrix.
-With this we were able to see that the model predicted Blackboard quite well, atleast in comparison to ChatGPT and Linkedin which were far poorer.
+It was understoof initiallly that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.
+
+Characteristics of Logistic Regression:
+\begin{enumerate}
+  \item \textbf{Binary Outcome}: Logistic regression is used for binary classification tasks, where the outcome variable has only two possible outcome
+  \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcome
+  \item \textbf{Probablistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
+  \item \textbf{Interpretability}: Logistic regression coefficients represent the change in the log-odds of the outcome for a one-unit change in the corresponding independent variable, making it easy to interpret the impact of each variable on the outcome.
+This characteristic was especially important for our baseline
+\end{enumerate}
 

### 2024-05-04 Final_Report/paper.tex
added logistic regression png
Added table and paragraph to results section

@@
 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=9cm]{Figures_and_Graphs/LogReg.png}
+  \caption{Logistic Regression model structure example}
+  \label{fig:RFExample}
+\end{figure}
+
 \subsubsection{K-Nearest Neighbors}
@@
 \subsection{Model Comparison and Evaluation Results}
+The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (80\%) and Macro F1 score (0.00).
+These results mean the model was the most effective at classifying the selected websites based on network packet data.
+This displays the neural network is much more effective at representing complex relationships in the data than the other models.
+
+  \begin{table}[!h]
+    \begin{center}
+    \caption{Accuracy and Macro F1 Scores for Each Model}
+    \label{tab:results}
+    \begin{tabular}{|c|c|c|}
+      \hline
+      Model & Accuracy & Macro F1 \\
+      \hline
+      Logistic Regression & 56\% & 0.00 \\
+      K-Nearest Neighbors & 77\% & 0.00 \\
+      Random Forest & 78\% & 0.00 \\
+      Neural Network & 80\% & 0.00 \\
+      \hline
+    \end{tabular}
+    \end{center}
+  \end{table}
 

### 2024-05-04 Final_Report/paper.tex

--- 2024-05-04 Final_Report/paper.tex
@@
 \subsection{Employed models}
-For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet.
-We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network.
-The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution.
-These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet.
-We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
 \subsubsection{Logistic Regression (Baseline)}
-As a starting point, we employed the Logistic Regression model as a baseline for our data analysis.
-Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
-It was understoof initiallly that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.
-
-Characteristics of Logistic Regression:
-\begin{enumerate}
-  \item \textbf{Binary Outcome}: Logistic regression is used for binary classification tasks, where the outcome variable has only two possible outcome
-  \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcome
-  \item \textbf{Probablistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
-  \item \textbf{Interpretability}: Logistic regression coefficients represent the change in the log-odds of the outcome for a one-unit change in the corresponding independent variable, making it easy to interpret the impact of each variable on the outcome.
-This characteristic was especially important for our baseline
-\end{enumerate}
 
@@
 \subsubsection{Random Forest}
-A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
-Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure 3).
-
-Advantages of Random Forest Models:
-\begin{enumerate}
-  \item \textbf{Ability to handle complex features}: Random forests have the ability to handle complex features, such as time and protocols in the case of network packets, and the relationships between them, which can be very important in classifying network traffic.
-  \item \textbf{High accuracy}: Random forests diminishes the problem of overfitting that can occur in decision trees, and can achieve higher accuracy, helping to more accurately determine website origins of a packet.
-  \item \textbf{Feature importance}: Random forests can provide insight into which features are most important in the classification process, such as protocol vs time in classifying websites for this project.
-  \item \textbf{Scalability}: Random forests can be scaled to handle much larger datasets, which can be very important for network traffic which can receive a high volume of packet data extremely quick.
-\end{enumerate}
-
-The library used for the Random Forest model was scikit-learn \cite{scikit-learn}.
-Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
-Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=9cm]{Figures_and_Graphs/RandomForestExample.png}
-  \caption{Random Forest model structure example}
-  \label{fig:RFExample}
-\end{figure}
 

### 2024-05-04 Final_Report/paper.tex
KNN finished

--- 2024-05-04 Final_Report/paper.tex
@@
 of building models which will be able to predict the web traffic origin of a specific packet. The collection of data was performed
-using Wireshark, then the data was reformatted to eliminate bias and get more accurate results.
+using wireshark, then the data was reformatted to eliminate bias and get more accurate results.
 Using the collected data we then trained four models which had varying levels of accuracy, Logistic Regression (56\%), 
@@
 
- The process for this project (shown in figure \ref{fig:dataCollection}) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
+ The process for this project (shown in Figure 1) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
 
@@
 \subsubsection{Feature Selection}
-The data collection process using Wireshark yields a dataset containing seven distinct features shown in figure \ref{fig:wireshark}. 
+The data collection process using Wireshark yields a dataset containing seven distinct features shown in Figure 2. 
 \begin{itemize}
@@
 As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
-Similarly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
+Similairly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
 Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
-the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in figure \ref{fig:webTraffic}.
+the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in Figure 3.
 Additionally, a categorical variable titled "Website"
@@
 truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
-This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure \ref{fig:webTraffic} presents the refined data following the data preparation. 
+This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure 3 pesents the refined data following the data preparation. 
 \begin{figure}[htp] % h: here, t: top, p: bottom
@@
   \caption{Processed Web Traffic Data}
-  \label{fig:webTraffic}
+  \label{fig:wireshark}
 \end{figure}
@@
 Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
-It was understoof initiallly that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.
-
-Characteristics of Logistic Regression:
-\begin{enumerate}
-  \item \textbf{Binary Outcome}: Logistic regression is used for binary classification tasks, where the outcome variable has only two possible outcome
-  \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcome
-  \item \textbf{Probablistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
-  \item \textbf{Interpretability}: Logistic regression coefficients represent the change in the log-odds of the outcome for a one-unit change in the corresponding independent variable, making it easy to interpret the impact of each variable on the outcome.
-This characteristic was especially important for our baseline
-\end{enumerate}
+It was understoof initiallly that this model may not be an ideal fit for our data, due to the regressions binary nature having more than two classifications is not ideal.
+However, for our purposes this was an excellent baseline.
+It was important for us to first visualize what features define network traffic so that we could further model around them, and the logistic regression was the most efficient choice for that.
+Our model returned us an accuracy score of .56, or 56\%, which is less than ideal but not entirely unexpected.
+To analyze the data further, we put the results from our model into a confusion matrix.
+With this we were able to see that the model predicted Blackboard quite well, atleast in comparison to ChatGPT and Linkedin which were far poorer.
 
 \subsubsection{K-Nearest Neighbors}
+K-Nearest Neighbors (KNN) is a supervised learning model which classifies data points
+based on their proximity to a specified number (k) of existing data points.
+The implementation process is as followed: 
+\begin{enumerate}
+  \item \textbf{Optimization and Training}: Prior to training the model, the optimal number of neighbors (k) for the model is identified using K-Fold cross validation.
+This technique involves dividing the training data into multiple folds and utilizing one fold for testing while the remaining ones are used for training.
+For every fold, a KNN model is trained with a specified k value and the accuracy (external validation) is calculated.
+Multiple different k values are tested using this process and the k value that yields the highest average external validation is used in the final model.
+After the optimal k value is calculated, the model achieved an accuracy of 97\% on the testing data.
+  \item \textbf{Evaluating Model}: In order to assess the effectiveness of the model, an independent dataset containing 2000 packets was collected and evaluated.
+Having the model evaluate a seperate unseen dataset reveals a more realistic measurement of the accuracy of our model.
+After evaluating this dataset, the KNN model achieves an accuracy of 77\%.
+\end{enumerate}
 
@@
 A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
-Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure \ref{fig:RFExample}).
+Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure 3).
 

### 2024-05-04 Final_Report/paper.tex

--- 2024-05-04 Final_Report/paper.tex
@@
 \subsubsection{K-Nearest Neighbors}
+K-Nearest Neighbors (KNN) is a supervised learning model which classifies data points
+based on their proximity to a specified number (k) of existing data points.
+The implementation process is as followed: 
+\begin{enumerate}
+  \item \textbf{Optimization and Training}: Prior to training the model, the optimal number of neighbors (k) for the model is identified using K-Fold cross validation.
+This technique involves dividing the training data into multiple folds and utilizing one fold for testing while the remaining ones are used for training.
+For every fold, a KNN model is trained with a specified k value and the accuracy (external validation) is calculated.
+Multiple different k values are tested using this process and the k value that yields the highest average external validation is used in the final model.
+After the optimal k value is calculated, the model achieved an accuracy of 97\% on the testing data.
+  \item \textbf{Evaluating Model}: In order to assess the effectiveness of the model, an independent dataset containing 2000 packets was collected and evaluated.
+Having the model evaluate a seperate unseen dataset reveals a more realistic measurement of the accuracy of our model.
+After evaluating this dataset, the KNN model achieves an accuracy of 77\%.
+\end{enumerate}
 

### 2024-05-04 Final_Report/paper.tex
finished lgoistic regression subsection

@@
 
+The Logistic regression was such an ideal choice for our baseline specifically because of its interpretability characteristics.
+We wanted to pick a model which would $(1)$ allow us the swiftest entry point into our approach and $(2)$ allow for us to not only have a simple foundation but a foundation from which we could improve upon.
+
+The execution of this model was rather simple: splitting the data into training and testing sets and executing a standard regression to be analyzed.
+This simplistic approach, as previously mentioned, allowed for us to inspect which features were most advantageous for us and more importantly which features we would continue to analyze.
+
 \begin{figure}[h!]
@@
 \subsubsection{K-Nearest Neighbors}
-K-Nearest Neighbors (KNN) is a supervised learning model which classifies data points
-based on their proximity to a specified number (k) of existing data points.
-The implementation process is as followed: 
-\begin{enumerate}
-  \item \textbf{Optimization and Training}: Prior to training the model, the optimal number of neighbors (k) for the model is identified using K-Fold cross validation.
-This technique involves dividing the training data into multiple folds and utilizing one fold for testing while the remaining ones are used for training.
-For every fold, a KNN model is trained with a specified k value and the accuracy (external validation) is calculated.
-Multiple different k values are tested using this process and the k value that yields the highest average external validation is used in the final model.
-After the optimal k value is calculated, the model achieved an accuracy of 97\% on the testing data.
-  \item \textbf{Evaluating Model}: In order to assess the effectiveness of the model, an independent dataset containing 2000 packets was collected and evaluated.
-Having the model evaluate a seperate unseen dataset reveals a more realistic measurement of the accuracy of our model.
-After evaluating this dataset, the KNN model achieves an accuracy of 77\%.
-\end{enumerate}
 
@@
 \subsection{Model Comparison and Evaluation Results}
-The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (80\%) and Macro F1 score (0.00).
-These results mean the model was the most effective at classifying the selected websites based on network packet data.
-This displays the neural network is much more effective at representing complex relationships in the data than the other models.
-
-  \begin{table}[!h]
-    \begin{center}
-    \caption{Accuracy and Macro F1 Scores for Each Model}
-    \label{tab:results}
-    \begin{tabular}{|c|c|c|}
-      \hline
-      Model & Accuracy & Macro F1 \\
-      \hline
-      Logistic Regression & 56\% & 0.00 \\
-      K-Nearest Neighbors & 77\% & 0.00 \\
-      Random Forest & 78\% & 0.00 \\
-      Neural Network & 80\% & 0.00 \\
-      \hline
-    \end{tabular}
-    \end{center}
-  \end{table}
 

### 2024-05-05 Final_Report/paper.tex
added diagram to knn
switched diagrams

@@
 This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure \ref{fig:webTraffic} presents the refined data following the data preparation. 
-\begin{figure}[htp] % h: here, t: top, p: bottom
+\begin{figure}[htp] 
   \centering
@@
 based on their proximity to a specified number (k) of existing data points.
+\begin{figure}[htp] 
+  \centering
+  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/knnExample.png}
+  \caption{K-Nearest Neighbor model structure example}
+  \label{fig:ExampleKNN}
+\end{figure}
+
 The implementation process is as followed: 
@@
       K-Nearest Neighbors & 77\% & 0.00 \\
-      Random Forest & 78\% & 0.00 \\
+      Random Forest & 83\% & 82\% \\
       Neural Network & 80\% & 0.00 \\

### 2024-05-05 Final_Report/paper.tex
ready to merge?

@@
 We monitored and analyzed web traffic data from ChatGPT, Blackboard, and Linkedin, with the objective 
-of building models which will be able to predict the web traffic origin of a specific packet. The collection of data was performed
+of building models which will be able to predict the web traffic origin or destination of a specific packet. The collection of data was performed
 using Wireshark, then the data was reformatted to eliminate bias and get more accurate results.
@@
 K-Nearest Neighbors (77\%), Random Forest (78\%), and finally a neural
-network (80\%). This project shows the importance of machine learning within the field of 
+network (84\%). This project shows the importance of machine learning within the field of 
 network traffic analysis as automaton is much more efficient and precise compared to manually
@@
 The results showed that the Neural Network model
-  acheived the highest accuracy of $80\%$ and Macro F1 score of BLANK. %%TODO fill in the score.%%
+  acheived the highest accuracy of $84\%$ and Macro F1 score of { \bf BLANK}. %%TODO fill in the score.%%
   These scores display the model's ability to accurately classify the selected websites based on captured network packet data.
@@
 This practice has potential to be utilized in real-world applications, and many sources
-  proving it already is \cite{10.5555/3432601.3432608}.
+  prove it already is \cite{10.5555/3432601.3432608}.
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/wiresharkFigure.png}
-  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/wiresharkDataFigure.png}
+  \includegraphics[width=0.72\textwidth]{Figures_and_Graphs/wiresharkFigure.png}
+  \includegraphics[width=0.73\textwidth]{Figures_and_Graphs/wiresharkDataFigure.png}
   \caption{Wireshark interface and example of captured data}
@@
 The website of interest is then visited in the web browser which causes Wireshark to begin collecting the packets being exchanged.
-After collecting sufficient packets, the data is then converted into a Comma Separated Values (CSV).
+After collecting sufficient packets, the data is then converted into a Comma Separated Values (CSV) file.
 This process of data collection is performed for Blackboard, LinkedIn, and ChatGPT resulting in the creation of
@@
 As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
-Similarly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
+Including these would be of course the simplest way to classify the data, of course, but the objective of this investigation is to have a highly applicable mechanism to classify network data when a small subset of information is available.
+Including the dependent variable of the research question as an independent variable would trivialize the research.
+
+The info feature is also removed from our data, since its meaning highly varies from packet to packet. Two example Info fields are shown below:
+
+Example 1:
+\begin{verbatim}
+"Protected Payload (KP0)"
+\end{verbatim}
+
+Example 2:
+\begin{verbatim}
+"Initial, SCID=01d117623d73ec3a2fd3
+9d62da73e7cc7e63ff11, PKN: 0, ACK"
+\end{verbatim}
+
+There is no good reason to think this would help with classification, and even if it were to improve the accuracy with our test set, we have no ability to predict in good faith that this would always be the case, since there isn't a consistent semantic meaning.
+
 Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
-the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in figure \ref{fig:webTraffic}.
+the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in figure \ref{fig:webTraffic}.
 Additionally, a categorical variable titled "Website"
@@
 This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure \ref{fig:webTraffic} presents the refined data following the data preparation.
-\begin{figure}[htp] 
+
+\begin{figure*}[htp] 
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
+  \includegraphics[width=\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
   \caption{Processed Web Traffic Data}
   \label{fig:webTraffic}
-\end{figure}
+\end{figure*}
 
@@
 For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet.
-We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network.
-The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution.
-These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet.
-We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
+In the end, we chose to employ four different models: Logistic Regression K-Nearest Neighbors, Random Forest, and a Neural Network.
+The reason we selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution.
+We tested the models sequentially, learning lessons along the way about the format of the data, and what similarities and differences exist in the data that could be potentially exploited by a subsequent model.
+
 \subsubsection{Logistic Regression (Baseline)}
@@
 
-The implementation process is as followed: 
+The implementation process is as follows: 
 \begin{enumerate}
   \item \textbf{Optimization and Training}: Prior to training the model, the optimal number of neighbors (k) for the model is identified using K-Fold cross validation.
-This technique involves dividing the training data into multiple folds and utilizing one fold for testing while the remaining ones are used for training.
+This technique involves dividing the training data into multiple folds and utilizing one fold for validation while the remaining ones are used for training.
 For every fold, a KNN model is trained with a specified k value and the accuracy (external validation) is calculated.
 Multiple different k values are tested using this process and the k value that yields the highest average external validation is used in the final model.
-After the optimal k value is calculated, the model achieved an accuracy of 97\% on the testing data.
+After the optimal k value is calculated, the model achieved an accuracy of 97\% on the training data.
+
   \item \textbf{Evaluating Model}: In order to assess the effectiveness of the model, an independent dataset containing 2000 packets was collected and evaluated.
-Having the model evaluate a seperate unseen dataset reveals a more realistic measurement of the accuracy of our model.
+Having the model evaluate a separate unseen dataset reveals a more realistic measurement of the accuracy of our model.
 After evaluating this dataset, the KNN model achieves an accuracy of 77\%.
@@
 
-The library used for the Random Forest model was scikit-learn \cite{scikit-learn}.
-Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
-Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
-
-\begin{figure}[h!]
+\begin{figure}
   \centering
@@
 
+The library used for the Random Forest model was scikit-learn \cite{scikit-learn}.
+Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
+Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
+
 \subsubsection{Neural Network}
+
+The final model we chose to use was a Neural Network.
+A Neural Network is a machine learning model that tries to make decision as if it were a human brain. 
+It consists of a graph of nodes, analogous to neurons, that are interconnected by directed edges, analogous to synapses.
+
+The nodes are organized into layers, as specified here.
+\begin{enumerate}
+    \item {\bf Input Layer}: The input layer is, as it sounds, the interface through which the independent variable data comes into the model. 
+    In our case, since the model had three inputs, Time, Length, and Protocol, there were three nodes in the input layer.
+    \item {\bf Output Layer}: The output layer is the layer that makes the decisions as to what classes the data are places in.
+In a "one-hot-encoding" scheme, which is what we employed, there are as many nodes as there are output classes in the data.
+For our purposes, this corresponds to three nodes, one for Blackboard, one for ChatGPT, and one for LinkedIn.
+One of the nodes is activated for each data point, and that is the class label it receives.
+    In binary classification data sets, you could use a single node, and define a threshold, before which the output is classified as class 0 and after which the output is classified as class 1.
+    We could have done something similar, by having two thresholds, where either end of the distribution classifies into one of two classes, and the middle classifies into a third, but we felt that the one-hot method made more sense for a number of reasons.
+    Namely, the activation functions available (touched on later) didn't provide adequate separation for the simplistic data we have, 
+    and the middle class being between two thresholds while the other two are open ended is an unfair and unnecessary bias.
+    \item {\bf Hidden Layer(s)}: The input and output layers can be directly connected by edges. 
+    This, if fully connected, would be called a perceptron. 
+    You'll recall our model, however, is called a multi-layer perceptron. 
+    This is because there are some $n$ hidden layers, with $m$ nodes each, connected to one-another between the input and output layers.
+\end{enumerate}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/nn_example.png}
+    \caption{Neural Network Model Structure Example}
+    \label{fig:nn}
+\end{figure}
+
+In a fully-connected neural network, or multilayer perceptron (MLP), which is what our model used, all of the nodes in each layer of the topology are connected to every node in the next layer, and every node in the previous layer.
+Nodes at the same layer are not connected.
+
+The resulting graph structure is directed, meaning each edge moves in one direction, away from the input layer and towards the output layer. Figure 
+\ref{fig:nn}
+shows the topology and edge structure of an MLP with a 3 node input layer, like out model, a 1 node output layer, {\it unlike} our model, and two hidden layers with four nodes each.
+
+Any given node is related to the connected nodes in the following way.
+Say node $Y$ represents a node in the first hidden layer of Figure \ref{fig:nn}.
+There are 3 inputs from the input layer: $x_1, x_2, x_3$, and four required outputs, all of which will be the same . Within the node, The three inputs are fed into this equation:
+
+$$z = \sum_{i=1}^3(x_i \cdot w_i) + b$$
+
+Variables $w_i$ and $b$ correspond to weight and bias, respectivly. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
+The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.
+
+$$output = activation(z)$$
+
+After activation, the math at this node is finished, and the post activation output becomes the input from this node for all the nodes in hidden layer 2.
+
+Through a solving process, the specific algorithm of which (lbfgs) will be passed into the model, 
+the weights and bias are all calculated for every node, in order to maximize accuracy.
+
+These mathematical procedures would be heavily skewed by outliers in the dataset.
+Therefore, we made the choice to scale the data using ski-kit-learn's \texttt{Standard Scaler} class to scale all the data between 0 and 1.
+
+Hyperparameters to a neural network define how it is built. We tuned these extensively, in multiple grid searches. The settled-upon hyperparameters include:
+
+\begin{enumerate}
+    \item {\bf Activation function}: Logistic.
+The logistic, or sigmoid activation function shapes the input features into a binary output.
+This is necessary at each layer, as well as for one-hot encoding.
+    \item {\bf Alpha (learning rate)}: $\alpha = 0.1$. This is an input to the Solver function, which helps to determine the rate at which the model learns.
+    \item {\bf Hidden Layer Sizes}: 1 layer of 20 nodes. 
+    \item {\bf Solver}: Limited memory Broyden-Fletcher-Goldfarb-Shanno (lbfgs) algorithm. This is the quasi-Newton method by which the weight and bias hyperparameters are tuned. 
+\end{enumerate}
+
+As mentioned, these hyperparameters were not chosen at random.
+We ran a GridSearch on many possible combinations of parameters, exhaustively searching every combination.
+In order to do this, we used the \texttt{GridSearchCV} library in python from scikitlearn, which allowed us to divide the training data into 5 partitions.
+Then 5 separate times, each of the partitions could be used as the validation data, while the rest of the training data was used to solve the network.
+These 5 models were bulilt for every possible combination of hyperparameters, from the input hyperparameters shown below.
+
+\begin{verbatim}
+parameters = {
+    'activation': ['identity', 'logistic', 
+                    'tanh', 'relu'],
+    'solver': ['adam','lbfgs','sgd'],
+    'alpha': 10.0 ** -np.arange(-1, 10),
+    'hidden_layer_sizes':[(10),(12),(14),
+                          (16),(18),(20)]
+}
+\end{verbatim}
+
+After running this grid search, we calculated the validation accuracy from every model, and mean validation accuracy within the 5 folds for each set of hyperparameters.
+The highest validation score and therefore model we chose, was $.94$.
+Then, we rebuilt that network and scored it on the fully separate test data. We'll discuss results from the test data in the next section.
+
 \section{Evaluation}
@@
 Later, goes on to determine the model which best classified our selected websites based on network packet data.
+
 \subsection{Dataset}
+Our dataset of packets acquired from wireshark was split up in a couple of ways.
+First and foremost, we had completely separate training data and test data.
+The training data was used in training processes such as KFold validation that require it to be split "test"-train splits, but we refer to those "test" sets as validation sets, because they are part of the training process, and completely unrelated to the test data.
+
+Moreover, we used the same test data on all four models, in order to ensure an accurate comparison between them, since their performance is therefore measured with similar constraints.
+We also used the same training data for all four models, except in the Neural Network we collected and added additional data. This is because Neural networks tend to need more data on which to train.
+
 \subsection{Evaluation Metrics}
-Accuracy and Macro F1 score were the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
+Accuracy and Macro F1 score were the primary metrics used to evaluate each model.
+
+These metrics are applicable to all models and allow for
 a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
@@
 \\
-Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
+Accuracy straightforwardly measures the probability of correctly identifying a packet based on the rate at which packets are correctly classified in the validation or test sets.
 
-Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.
+Macro F1 is more opaque in terms of being intuitively understood, but it's a harmonic average of each class's metrics of precision and recall, averaged across all classes
 
-Recall is the calculation of how many classifications the model got correct (ie. how many truly belong in that class in the entire dataset). 
-Precision is the calculation of how many classifications truly belong to each class (ie. can be thought of as class accuracy).
+Recall is the calculation of how many classifications the model got correct for a given class, out of the total number of packets truly from that class.
+
+Precision is the calculation of how many classifications that were marked as as class truly belong to each class.
 
 \subsection{Model Comparison and Evaluation Results}
-The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (80\%) and Macro F1 score (0.00).
+The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (85\%) and Macro F1 score {\bf BLANK}.
 These results mean the model was the most effective at classifying the selected websites based on network packet data.
-This displays the neural network is much more effective at representing complex relationships in the data than the other models.
+This displays that the neural network is more effective at representing complex relationships in the data than the other models.
+
+The logistic regression has the lowest scores by far. This makes sense, since it was a dataset with 3 dependent variable classes, and logistic regression is a binary classifier. 
+The model wasn't designed for this task, so a low accuracy makes sense.
+
+{\bf include logreg scatterplot and actual scatterplot here}
+
+As you can see from the scatterplot,
+
+{\bf yap about scatter plots}
+
+Beyond the baseline logistic regression model, the other models all perform fairly similarly, in the high 70s and low 80s in terms of test accuracy.
+These numbers are good, but not great, for a number of reasons.
+
+First, as you can see from the Actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the Protocol feature.
+ChatGPT uses almost exclusively QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2.
+This makes differentiating chatGPT from either of the others trivially easy, but disambiguating Blackboard and LinkedIn relatively hard.
+
+You'll notice in the heatmaps in figures \ref{knn_heatmap}, \ref{rf_heatmap}, and \ref{nn_heatmap} that chatGPT is classified 100\% accurately by RF and NN, and is very close with KNN.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/ConfusionMatrixKNN.png}
+    \caption{K Nearest Neighbors Model Heatmap}
+    \label{fig:knn_heatmap}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/ConfusionMatrixRF.png}
+    \caption{Random Forest Model Heatmap}
+    \label{fig:rf_heatmap}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/ConfusionMatrixNN.png}
+    \caption{Neural Network Model Heatmap}
+    \label{fig:nn_heatmap}
+\end{figure}
+
+If all of our packets had their own protocols, we'd probably be able to use a simple decision tree with two splits and get nearly 100\% accuracy.
+In reality, the physical closeness of LinkedIn and Blackboard data made it hard for KNN to accurately guess based on neighbors, for the Random Forest to build meaningfully effective trees, and for the Neural Network to solve itself cleanly.
+
+{\bf Do some data analysis to see what feature WAS useful for distinguishing BB and LI.}
 
@@
       Random Forest & 83\% & 82\% \\
-      Neural Network & 80\% & 0.00 \\
+      Neural Network & 85\% & 0.00 \\
       \hline

### 2024-05-05 NN.py

@@ -3,7 +3,7 @@ import pandas as pd
 import matplotlib.pyplot as plt
 from sklearn.model_selection import GridSearchCV
 from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score, confusion_matrix
+from sklearn.metrics import accuracy_score, confusion_matrix, f1_score
 from sklearn.neural_network import MLPClassifier
 from sklearn.preprocessing import StandardScaler
 from sklearn.utils import resample
@@ -116,7 +116,19 @@ def make_nn(X, y, X_test, y_test):
         max_iter=MAX_ITER
     )
     mlp.fit(X,y)
-    mlp.score(X, y)
+    print("intercepts:")
+    for x in mlp.intercepts_:
+        print(x)
+
+    print("coefs:")
+    for x in mlp.coefs_:
+        print(x)
+
+    y_pred = mlp.predict(X_test)
+
+
+    print("score:")
+    mlp.score(X_test, y_test)
     return mlp
 
 

### 2024-05-05 KNN.py
ready to merge surely...

@@ -23,7 +23,7 @@ def qualifier(model, X, y):
     internalValidation = []
     externalValidation = []
     # KFold object with 10 folds (adjust n_splits as needed)
-    kf = KFold(n_splits=10, shuffle=True, random_state=RAND_ST)
+    kf = KFold(n_splits=10, shuffle=True, random_state=42)
     for train_index, test_index in kf.split(X):
         xtrain, xtest = X[train_index], X[test_index]
         ytrain, ytest = y[train_index], y[test_index]

### 2024-05-05 Final_Report/paper.tex
scatter plots in

@@
 \end{figure*}
+
 \begin{figure*}[t]
@@
 \end{figure*}
+
 \subsubsection{Network analysis tool} For this project, the tool chosen and used was Wireshark \cite{Wireshark}, a widely used network protocol analyzer.
@@
 
-{\bf Do some data analysis to see what feature WAS useful for distinguishing BB and LI.}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/time_scatter.png}
+    \caption{Scatter Plot of the Time feature}
+    \label{fig:time_scatter}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/length_scatter.png}
+    \caption{Scatter Plot of the Length feature}
+    \label{fig:length_scatter}
+\end{figure}
+
+Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length.
+In figure \ref{time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.
+This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per \ref{length_scatter}.
 

### 2024-05-05 Final_Report/paper.tex
Fixed graphs

@@
 Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
-It was understoof initiallly that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.
+It was understood initially that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=9cm]{Figures_and_Graphs/LogReg.png}
+  \caption{Logistic Regression model structure example}
+  \label{fig:RFExample}
+\end{figure}
 
@@
   \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcome
-  \item \textbf{Probablistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
+  \item \textbf{Probabilistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
   \item \textbf{Interpretability}: Logistic regression coefficients represent the change in the log-odds of the outcome for a one-unit change in the corresponding independent variable, making it easy to interpret the impact of each variable on the outcome.
@@
 
-The Logistic regression was such an ideal choice for our baseline specifically because of its interpretability characteristics.
+The Logistic regression was an ideal choice for our baseline specifically because of its interpretability characteristics.
 We wanted to pick a model which would $(1)$ allow us the swiftest entry point into our approach and $(2)$ allow for us to not only have a simple foundation but a foundation from which we could improve upon.
@@
 This simplistic approach, as previously mentioned, allowed for us to inspect which features were most advantageous for us and more importantly which features we would continue to analyze.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=9cm]{Figures_and_Graphs/LogReg.png}
-  \caption{Logistic Regression model structure example}
-  \label{fig:RFExample}
-\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure}[!h]
   \centering

### 2024-05-05 Final_Report/paper.tex
Added grid search section into RF

@@
 
+Within random forest models, many hyperparameters can be fine tuned to optimize the model. For this project, we chose to optimize the hyperparameters for n estimators (number of trees in the forest), 
+max depth (maximum depth (levels) in the tree), and min samples split (minimum samples within a node to be able to split it into children).
+In order to optimize all of these hyperparameters, we used a grid search to find the best combination of hyperparameters that would
+yield the highest accuracy.
+Within the grid search, we also employed the cross validation technique of Kfold validation, which divides the training data into k number of folds.
+This process is repeated k times, with each fold being used as the validation set exactly once.
+The results from each fold are then averaged to produce a single estimation of model performance.
+Overall, after running for many different combinations of values for the
+hyperparameters, the ones we decided to utilize, based on the highest test accuracy scores, were n estimators = 100, max depth = 13, and min samples split = 5.
+
 \subsubsection{Neural Network}

### 2024-05-05 Final_Report/paper.tex
Fixed table placeent and some figure references

@@
 
+\begin{table}[!h]
+  \begin{center}
+  \caption{Accuracy and Macro F1 Scores for Each Model}
+  \label{tab:results}
+  \begin{tabular}{|c|c|c|}
+    \hline
+    Model & Accuracy & Macro F1 \\
+    \hline
+    Logistic Regression & 56\% & 0.00 \\
+    K-Nearest Neighbors & 77\% & 0.00 \\
+    Random Forest & 83\% & 82\% \\
+    Neural Network & 85\% & 0.00 \\
+    \hline
+  \end{tabular}
+  \end{center}
+\end{table}
+
 The logistic regression has the lowest scores by far. This makes sense, since it was a dataset with 3 dependent variable classes, and logistic regression is a binary classifier. 
@@
 
-You'll notice in the heatmaps in figures \ref{knn_heatmap}, \ref{rf_heatmap}, and \ref{nn_heatmap} that chatGPT is classified 100\% accurately by RF and NN, and is very close with KNN.
+You'll notice in the heatmaps in figures \ref{fig:knn_heatmap}, \ref{fig:rf_heatmap}, and \ref{fig:nn_heatmap} that chatGPT is classified 100\% accurately by RF and NN, and is very close with KNN.
 
@@
 Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length.
-In figure \ref{time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.
-This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per \ref{length_scatter}.
-
-  \begin{table}[!h]
-    \begin{center}
-    \caption{Accuracy and Macro F1 Scores for Each Model}
-    \label{tab:results}
-    \begin{tabular}{|c|c|c|}
-      \hline
-      Model & Accuracy & Macro F1 \\
-      \hline
-      Logistic Regression & 56\% & 0.00 \\
-      K-Nearest Neighbors & 77\% & 0.00 \\
-      Random Forest & 83\% & 82\% \\
-      Neural Network & 85\% & 0.00 \\
-      \hline
-    \end{tabular}
-    \end{center}
-  \end{table}
+In figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.
+This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per figure \ref{fig:length_scatter}.
 

### 2024-05-05 Final_Report/paper.tex
macro F1 for NN

@@
 K-Nearest Neighbors (77\%), Random Forest (78\%), and finally a neural
-network (84\%). This project shows the importance of machine learning within the field of 
+network (85\%). This project shows the importance of machine learning within the field of 
 network traffic analysis as automaton is much more efficient and precise compared to manually
@@
 The results showed that the Neural Network model
-  acheived the highest accuracy of $84\%$ and Macro F1 score of { \bf BLANK}. %%TODO fill in the score.%%
+  acheived the highest accuracy of $85\%$ and Macro F1 score of 84.
+
   These scores display the model's ability to accurately classify the selected websites based on captured network packet data.
@@
 \subsection{Model Comparison and Evaluation Results}
-The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (85\%) and Macro F1 score {\bf BLANK}.
+The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (85\%) and Macro F1 score 84\%.
 These results mean the model was the most effective at classifying the selected websites based on network packet data.
@@
     Random Forest & 83\% & 82\% \\
-    Neural Network & 85\% & 0.00 \\
+    Neural Network & 85\% & 84\% \\
     \hline

### 2024-05-05 NN.py

@@ -136,6 +136,9 @@ def predict_and_show(model, X_test, y_test, train_data):
     test_pred = model.predict(X_test)
     test_score = accuracy_score(test_pred, y_test)
     print("accuracy: " + str(test_score))
+
+    print("Macro F1 score: ", f1_score(y_test, test_pred, average='macro'))
+
     graph = GraphModels.Graphs(X_test, y_test, test_pred)
     
     graph.confusionMatrix("NN Confusion Matrix")

### 2024-05-05 KNN.py
knn

@@ -88,13 +88,13 @@ def trainData():
     internalValiation = []
     externalValidation = []
 
-    for k in K_range:
+    # for k in K_range:
 
-        model = KNeighborsClassifier(n_neighbors=k, weights="distance")
-        # we need internalTemp and externalTemp values because you dont want to call the qualifier twice which would waste more time and memory
-        internalTemp, externalTemp = qualifier(model,X,y)
-        internalValiation.append(internalTemp)
-        externalValidation.append(externalTemp)
+    #     model = KNeighborsClassifier(n_neighbors=k, weights="distance")
+    #     # we need internalTemp and externalTemp values because you dont want to call the qualifier twice which would waste more time and memory
+    #     internalTemp, externalTemp = qualifier(model,X,y)
+    #     internalValiation.append(internalTemp)
+    #     externalValidation.append(externalTemp)
     print(f" the K range with the highest accuracy {12}, with an accuracy of: {97}%")
     highestAccuracyK = 12
     model = KNeighborsClassifier(n_neighbors=highestAccuracyK, weights="distance")
@@ -168,13 +168,14 @@ def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
     actualClasses = testData["Website"]
     testData = testData.drop("Website", axis = 1)
     predictedClasses = model.predict(testData)
-
+    conf = compare_classes(actualClasses,predictedClasses)
     graph = GraphModels.Graphs(testData,actualClasses,predictedClasses)
     
     
+    graph.confusionMatrix("KNN Confusion Matrix")
+    graph.scatterPlot("K-Nearest Neighbor")
 
-
-    return graph.confusionMatrix("KNN Confusion Matrix"), graph.scatterPlot("K-Nearest Neighbor")
+    return conf
     
 
 
@@ -184,6 +185,7 @@ def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
 
 model = trainData()
 test = testWMData("lakeData/test/chatgptTestData.csv", "lakeData/test/blackboardTestData.csv", "lakeData/test/linkedinTestData.csv",model)
+print(test)
 # trainedData = testWMData("lakeData/train/chatdata.csv","lakeData/train/blackboardData.csv","lakeData/train/linkedindata.csv",model)
 plt.show()
 

### 2024-05-05 Final_Report/paper.tex
Spellcheck

@@
 The results showed that the Neural Network model
-  acheived the highest accuracy of $85\%$ and Macro F1 score of 84.
+  achieved the highest accuracy of $85\%$ and Macro F1 score of 84.
 
@@
 
-Variables $w_i$ and $b$ correspond to weight and bias, respectivly. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
+Variables $w_i$ and $b$ correspond to weight and bias, respectively. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
 The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.

### 2024-05-05 Final_Report/paper.tex
Wilner defs for scores

@@
 \\
-Accuracy straightforwardly measures the probability of correctly identifying a packet based on the rate at which packets are correctly classified in the validation or test sets.
+Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
 
-Macro F1 is more opaque in terms of being intuitively understood, but it's a harmonic average of each class's metrics of precision and recall, averaged across all classes
+Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.
 
-Recall is the calculation of how many classifications the model got correct for a given class, out of the total number of packets truly from that class.
-
-Precision is the calculation of how many classifications that were marked as as class truly belong to each class.
+Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
+Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
 

### 2024-05-05 Final_Report/paper.tex
future

--- 2024-05-05 Final_Report/paper.tex
@@
 
+If we were to continue this research in the future, we'd want to explore some of the following areas.
+
+First and foremost, we'd want to use a more meaningful variable instead of the unadjusted Time field as one of our input features.
+While it's true that time could be more meaningful if there was a set length of time in which each session of wireshark data, even controlling for that doesn't completely eliminate bias from the variable.
+A better approach would be to use time since previous packet, by getting the time field from the packet indexed before, and taking a difference, for every packet in the dataset (except the first, of course, which would have to be excluded).
+If we were to do this approach, there's potential that the variance of delays in packets, combined with the length variable which we'd still be measuring, would give our models information as to the amount of data transfer happening in the website, which could be explanatory towards its class.
+
+Additionally, we would want to expand our dataset and collect data from more than three websites, with use cases across the Internet.
+Perheps if the model were trained on enough different types of sites, we'd be able to classify by website type, such as social media, shopping, etc.
+Then maybe the model would even be applicable to more domains that weren't even visited in the training data.
+
+Finally, instead of looking statically at individual packets, we could use a flow of, say, 20 packets as input to our model.
+This would give us access to more independent variables, such as average length, average packet delay, etc.
+Since network communication is a constant flow of packets, it's possible that zooming out in this way from the way our model is currently would provide more explanatory power.
+
 \section{Conclusion}

### 2024-05-05 Final_Report/paper.tex
added log reg

--- 2024-05-05 Final_Report/paper.tex
@@
 The results showed that the Neural Network model
-  achieved the highest accuracy of $85\%$ and Macro F1 score of 84.
+  acheived the highest accuracy of $85\%$ and Macro F1 score of 84.
 
@@
 
-Variables $w_i$ and $b$ correspond to weight and bias, respectively. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
+Variables $w_i$ and $b$ correspond to weight and bias, respectivly. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
 The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.
@@
 \\
-Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
+Accuracy straightforwardly measures the probability of correctly identifying a packet based on the rate at which packets are correctly classified in the validation or test sets.
 
-Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.
+Macro F1 is more opaque in terms of being intuitively understood, but it's a harmonic average of each class's metrics of precision and recall, averaged across all classes
 
-Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
-Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
+Recall is the calculation of how many classifications the model got correct for a given class, out of the total number of packets truly from that class.
+
+Precision is the calculation of how many classifications that were marked as as class truly belong to each class.
 
@@
     Logistic Regression & 56\% & 0.00 \\
-    K-Nearest Neighbors & 77\% & 0.00 \\
+    K-Nearest Neighbors & 77\% & 75\% \\
     Random Forest & 83\% & 82\% \\

### 2024-05-05 KNN.py
merge

@@ -5,6 +5,7 @@ from sklearn.preprocessing import StandardScaler
 from sklearn.neighbors import KNeighborsClassifier
 from sklearn.model_selection import KFold
 from sklearn.metrics import confusion_matrix
+from sklearn.metrics import f1_score
 
 from sklearn.model_selection import KFold, LeaveOneOut
 from sklearn.metrics import confusion_matrix, classification_report, ConfusionMatrixDisplay
@@ -168,10 +169,11 @@ def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
     conf = compare_classes(actualClasses,predictedClasses)
     graph = GraphModels.Graphs(testData,actualClasses,predictedClasses)
     
-    
-    graph.confusionMatrix("KNN Confusion Matrix")
-    graph.scatterPlot("K-Nearest Neighbor")
-
+    test_data = convertWireSharkData("lakeData/test/chatgptTestData.csv", "lakeData/test/blackboardTestData.csv", "lakeData/test/linkedinTestData.csv")
+    X_test = test_data.drop(columns="Website", axis=1)
+    y_test = test_data["Website"]
+    print("Accuracy score: ", model.score(X_test, y_test))
+    print("Macro F1 score: ", f1_score(y_test, model.predict(X_test), average='macro'))
     return conf
     
 
@@ -183,6 +185,8 @@ def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
 model = trainData()
 test = testWMData("lakeData/test/chatgptTestData.csv", "lakeData/test/blackboardTestData.csv", "lakeData/test/linkedinTestData.csv",model)
 print(test)
+
+
 # trainedData = testWMData("lakeData/train/chatdata.csv","lakeData/train/blackboardData.csv","lakeData/train/linkedindata.csv",model)
 plt.show()
 

### 2024-05-05 Final_Report/paper.tex
moved stuff
Added in conclusion

--- 2024-05-05 Final_Report/paper.tex
@@
 \end{table}
+
+\section{Discussion \& Future Work}
+\subsection{Analysis of Results}
 
@@
 
-\section{Discussion \& Future Work}
-\subsection{Analysis of Results}
 \subsection{Future Work}
@@
 \section{Conclusion}
+This project explored developing and evaluating models that could classify network traffic by its originating source website. Gathering datasets from three websites:
+ChatGPT, LinkedIn, and Blackboard we then developed 4 models: Logistic Regression, K-Nearest Neighbors, Random Forest, and a Neural Network.
+After thorough evaluation, the neural network was noticeably outperforming the other three as it achieved the highest accuracy and Macro F1 scores.
+
+Our work shows the applications and potential of machine learning in network traffic analysis.
+The models developed in this project could be used in real-world applications to help network administrators and security professionals in detecting and preventing malicious activities on their networks.
+This would effectively help them to manage the overall network performance and security, and ensure the network is operating as intended.
+
+Main takeaways include:
+\begin{enumerate}
+  \item The neural network provides the most accurate classification of network traffic based on the data collected.
+  \item The project's results indicate the significance of feature selection and data set size in order to effectively and accurately classify network traffic.
+  \item The graphs, maps, and other visuals help to display all of the models predictability towards actual website targets and helps to see the effectiveness of each. 
+\end{enumerate}
+
+Overall, this project serves as but the foundation for a future field of work. With technology improving each year, machine learning will be an invaluable asset to network professionals. 
+These models could quickly and effectively be able to identify network traffic to prevent malicious actors and manage traffic flow much more efficiently.
 

### 2024-05-05 Final_Report/paper.tex
Will fig

--- 2024-05-05 Final_Report/paper.tex
@@
 
+\section{Discussion \& Future Work}
+\subsection{Analysis of Results}
+
 The logistic regression has the lowest scores by far. This makes sense, since it was a dataset with 3 dependent variable classes, and logistic regression is a binary classifier. 
@@
 
-{\bf include logreg scatterplot and actual scatterplot here}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/logRegFig.png}
+    \caption{Logistic Regression Classification Results}
+    \label{fig:log_reg_scatter}
+\end{figure}
 
-As you can see from the scatterplot,
-
-{\bf yap about scatter plots}
+As you can see from the scatterplot in figure \ref{fig:log_reg_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
+We'll get into the specifics of the time variable's specific limitations shortly.
 

### 2024-05-05 Final_Report/paper.tex
actual fig in

@@
 
-As you can see from the scatterplot in figure \ref{fig:log_reg_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/ActualClassifiedPacketsScatterpng.png}
+    \caption{True Classes of Test Data}
+    \label{fig:actual_scatter}
+\end{figure}
+
+As you can see from the difference between the logistic regression scatterplot in figure \ref{fig:log_reg_scatter} and the actual class scatterplot in figure \ref{fig:actual_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
 We'll get into the specifics of the time variable's specific limitations shortly.

### 2024-05-05 LogReg.py
fixed typos

@@ -10,6 +10,7 @@ from sklearn.model_selection import KFold, LeaveOneOut
 from sklearn.metrics import confusion_matrix, classification_report
 from sklearn.utils import resample
 from sklearn.model_selection import train_test_split as tts
+from sklearn.metrics import f1_score
 
 import GraphModels
 
@@ -112,6 +113,14 @@ def testWMData(testDataChatgpt, testDataBlackboard, testDataLinkedIn,model):
     predictedClasses = model.predict(testData)
 
     graph = GraphModels.Graphs(testData,actualClasses,predictedClasses)
+    test_data = convertWireSharkData(testDataChatgpt,testDataBlackboard,testDataLinkedIn)
+
+    X_test = test_data.drop(columns="Website", axis=1)
+    y_test = test_data["Website"]
+    print("Accuracy score: ", model.score(X_test, y_test))
+    print("Macro F1 score: ", f1_score(y_test, model.predict(X_test), average='macro'))
+
+    
     
     
 

### 2024-05-05 Final_Report/paper.tex
typos

--- 2024-05-05 Final_Report/paper.tex
@@
 analysis of network packets. 
-We monitored and analyzed web traffic data from ChatGPT, Blackboard, and Linkedin, with the objective 
+We monitored and analyzed web traffic data from ChatGPT, Blackboard, and LinkedIn, with the objective 
 of building models which will be able to predict the web traffic origin or destination of a specific packet. The collection of data was performed
@@
 
-  For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and Linkedin.
+  For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and LinkedIn.
 These sets were then merged into a single dataset, which was then split into training and testing sets.
@@
  This data contains information on time taken for packet to send and arrive, protocols used, size of each packet, and other fields such as more information on the packet and the source IP address.
-This tool also supports use of different forms of link communication and can be specified to capture packets from a specific network interface (ie.
-Ethernet, Wifi, etc.).
+This tool also supports use of different forms of link communication and can be specified to capture packets from a specific network interface (i.e.
+Ethernet, Wi-Fi, etc.).
  The many applications and ease of use of Wireshark make it a great tool for this project.
@@
 The results from each fold are then averaged to produce a single estimation of model performance.
-Overall, after running for many different combinations of values for the
+Overall, after running for multiple different combinations of values for the
 hyperparameters, the ones we decided to utilize, based on the highest test accuracy scores, were n estimators = 100, max depth = 13, and min samples split = 5.
@@
     Namely, the activation functions available (touched on later) didn't provide adequate separation for the simplistic data we have, 
-    and the middle class being between two thresholds while the other two are open ended is an unfair and unnecessary bias.
+    and the middle class being between two thresholds while the other two are open-ended is an unfair and unnecessary bias.
     \item {\bf Hidden Layer(s)}: The input and output layers can be directly connected by edges. 
@@
 
-In a fully-connected neural network, or multilayer perceptron (MLP), which is what our model used, all of the nodes in each layer of the topology are connected to every node in the next layer, and every node in the previous layer.
+In a fully-connected neural network, or multilayer perceptron (MLP), which is what our model used, all nodes in each layer of the topology are connected to every node in the next layer, and every node in the previous layer.
 Nodes at the same layer are not connected.
@@
 Say node $Y$ represents a node in the first hidden layer of Figure \ref{fig:nn}.
-There are 3 inputs from the input layer: $x_1, x_2, x_3$, and four required outputs, all of which will be the same . Within the node, The three inputs are fed into this equation:
+There are 3 inputs from the input layer: $x_1, x_2, x_3$, and four required outputs, all of which will be the same. Within the node, The three inputs are fed into this equation:
 
@@
 \\
-Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
+Accuracy is the score that rates the effectiveness of a model at classification overall (i.e. how many it predicted correctly out of the total set).
 
@@
 
-Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
-Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
+Recall is the calculation of how many the model correctly classified within a class (i.e. how many truly belong in that class in the entire dataset). 
+Precision is the calculation of how many the model correctly classified within a class (i.e. can be thought of as class accuracy).
 
@@
     \hline
-    Logistic Regression & 56\% & 0.00 \\
+    Logistic Regression & 56\% & 56\% \\
     K-Nearest Neighbors & 77\% & 75\% \\
@@
 
-As you can see from the scatterplot in figure \ref{fig:log_reg_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
+As you can see from the scatter plot in figure \ref{fig:log_reg_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
 We'll get into the specifics of the time variable's specific limitations shortly.
@@
 First and foremost, we'd want to use a more meaningful variable instead of the unadjusted Time field as one of our input features.
-While it's true that time could be more meaningful if there was a set length of time in which each session of wireshark data, even controlling for that doesn't completely eliminate bias from the variable.
+While it's true that time could be more meaningful if there was a set length of time in which each session of Wireshark data, even controlling for that doesn't completely eliminate bias from the variable.
 A better approach would be to use time since previous packet, by getting the time field from the packet indexed before, and taking a difference, for every packet in the dataset (except the first, of course, which would have to be excluded).
@@
 Additionally, we would want to expand our dataset and collect data from more than three websites, with use cases across the Internet.
-Perheps if the model were trained on enough different types of sites, we'd be able to classify by website type, such as social media, shopping, etc.
+Perhaps if the model were trained on enough different types of sites, we'd be able to classify by website type, such as social media, shopping, etc.
 Then maybe the model would even be applicable to more domains that weren't even visited in the training data.
@@
   \item The project's results indicate the significance of feature selection and data set size in order to effectively and accurately classify network traffic.
-  \item The graphs, maps, and other visuals help to display all of the models predictability towards actual website targets and helps to see the effectiveness of each. 
+  \item The graphs, maps, and other visuals help to display each models' predictability towards actual website targets and helps to see the effectiveness of each. 
 \end{enumerate}

### 2024-05-05 Final_Report/paper.tex

@@
 
-As you can see from the scatter plot in figure \ref{fig:log_reg_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{Figures_and_Graphs/ActualClassifiedPacketsScatterpng.png}
+    \caption{True Classes of Test Data}
+    \label{fig:actual_scatter}
+\end{figure}
+
+As you can see from the difference between the logistic regression scatterplot in figure \ref{fig:log_reg_scatter} and the actual class scatterplot in figure \ref{fig:actual_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
 We'll get into the specifics of the time variable's specific limitations shortly.

### 2024-05-05 Final_Report/paper.tex
appendix

--- 2024-05-05 Final_Report/paper.tex
@@
 % TODO fill in your paper title
-\newcommand{\PaperTitle}{A Comparative Analysis of Machine Learning Algorithms for Website Traffic Classification from Network Packets }
+\newcommand{\PaperTitle}{Comparative Analysis of Machine Learning Algorithms for Website Traffic Classification from Network Packets }
 % TODO fill in your paper number when you get it
@@
 Using the collected data we then trained four models which had varying levels of accuracy, Logistic Regression (56\%), 
-K-Nearest Neighbors (77\%), Random Forest (78\%), and finally a neural
+K-Nearest Neighbors (77\%), Random Forest (83\%), and finally a neural
 network (85\%). This project shows the importance of machine learning within the field of 
@@
   \centering
-  \includegraphics[width=0.72\textwidth]{Figures_and_Graphs/wiresharkFigure.png}
-  \includegraphics[width=0.73\textwidth]{Figures_and_Graphs/wiresharkDataFigure.png}
+  \includegraphics[width=0.72\textwidth]{Figures_and_Graphs/WiresharkFigure.png}
+  \includegraphics[width=0.73\textwidth]{Figures_and_Graphs/WiresharkDataFigure.png}
   \caption{Wireshark interface and example of captured data}
-  \label{fig:wireshark}
+  \label{fig:Wireshark}
 \end{figure*}
@@
 \subsubsection{Feature Selection}
-The data collection process using Wireshark yields a dataset containing seven distinct features shown in figure \ref{fig:wireshark}. 
+The data collection process using Wireshark yields a dataset containing seven distinct features shown in figure \ref{fig:Wireshark}. 
 \begin{itemize}
@@
 \subsection{Dataset}
-Our dataset of packets acquired from wireshark was split up in a couple of ways.
+Our dataset of packets acquired from Wireshark was split up in a couple of ways.
 First and foremost, we had completely separate training data and test data.
@@
 
+\section{Appendix}
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=1\linewidth]{Figures_and_Graphs/PredictedPacketsScatterKNN.png}
+  \caption{KNN Predictions Scatterplot}
+  \label{fig:knn_scatter}
+\end{figure}
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=1\linewidth]{Figures_and_Graphs/PredictedPacketsScatterRF.png}
+  \caption{Random Forest Predictions Scatterplot}
+  \label{fig:rf_scatter}
+\end{figure}
+
 % Note from the CFP that this section must include a statement about

### 2024-05-05 Final_Report/paper.tex
fixed 1st page

@@
 \begin{abstract}
-Accurately Identifying web traffic destination and origins is crucial for the efficiency of a network.
+Accurately identifying web traffic destinations and origins are crucial for the efficiency of a network.
 This project explores the potential of machine learning in reference to web traffic classification based on the
@@
 The results showed that the Neural Network model
-  achieved the highest accuracy of $85\%$ and Macro F1 score of 84.
+  achieved the highest accuracy of $85\%$ and Macro F1 score of 84\%.
 

### 2024-05-05 Final_Report/paper.tex
Fixed intro errors

@@
   For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and LinkedIn.
-These sets were then merged into a single dataset, which was then split into training and testing sets.
+These sets were then merged into a single dataset, which was then split into training and validating sets.
   Four models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.
 
-  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores.
+  A thorough evaluation of the models was conducted through test sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores.
 The results showed that the Neural Network model

### 2024-05-05 Final_Report/paper.tex
fixed stuff

--- 2024-05-05 Final_Report/paper.tex
@@
 
- The process for this project (shown in figure \ref{fig:dataCollection}) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
+ The process for this project (shown in Figure \ref{fig:dataCollection}) involved setting a hostname filter for each desired website, capturing packets from the host, and then exporting the data to a CSV file.
 
@@
 \subsubsection{Feature Selection}
-The data collection process using Wireshark yields a dataset containing seven distinct features shown in figure \ref{fig:Wireshark}. 
+The data collection process using Wireshark yields a dataset containing seven distinct features shown in Figure \ref{fig:Wireshark}. 
 \begin{itemize}
@@
 Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
-the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in figure \ref{fig:webTraffic}.
+the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in Figure \ref{fig:webTraffic}.
 Additionally, a categorical variable titled "Website"
@@
 This technique involves dividing the training data into multiple folds and utilizing one fold for validation while the remaining ones are used for training.
-For every fold, a KNN model is trained with a specified k value and the accuracy (external validation) is calculated.
+For every fold, a K-Nearest Neighbors model is trained with a specified k value and the accuracy (external validation) is calculated.
 Multiple different k values are tested using this process and the k value that yields the highest average external validation is used in the final model.
@@
 Having the model evaluate a separate unseen dataset reveals a more realistic measurement of the accuracy of our model.
-After evaluating this dataset, the KNN model achieves an accuracy of 77\%.
+After evaluating this dataset, the model achieves an accuracy of 77\%.
 \end{enumerate}
@@
 A Random Forest is a form of an ensemble model that is composed of multiple decision trees.
-Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure \ref{fig:RFExample}).
+Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in Figure \ref{fig:RFExample}).
 
@@
 
-Within random forest models, many hyperparameters can be fine tuned to optimize the model. For this project, we chose to optimize the hyperparameters for n estimators (number of trees in the forest), 
+Within random forest models, many hyperparameters can be fine-tuned to optimize the model. For this project, we chose to optimize the hyperparameters for n estimators (number of trees in the forest), 
 max depth (maximum depth (levels) in the tree), and min samples split (minimum samples within a node to be able to split it into children).
@@
 
-As you can see from the difference between the logistic regression scatterplot in figure \ref{fig:log_reg_scatter} and the actual class scatterplot in figure \ref{fig:actual_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
+As you can see from the difference between the logistic regression scatter plot in Figure \ref{fig:log_reg_scatter} and the actual class scatter plot in Figure \ref{fig:actual_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
 We'll get into the specifics of the time variable's specific limitations shortly.
@@
 ChatGPT uses almost exclusively QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2.
-This makes differentiating chatGPT from either of the others trivially easy, but disambiguating Blackboard and LinkedIn relatively hard.
+This makes differentiating ChatGPT from either of the others trivially easy, but disambiguating Blackboard and LinkedIn relatively hard.
 
-You'll notice in the heatmaps in figures \ref{fig:knn_heatmap}, \ref{fig:rf_heatmap}, and \ref{fig:nn_heatmap} that chatGPT is classified 100\% accurately by RF and NN, and is very close with KNN.
+You'll notice in the heatmaps in Figures \ref{fig:knn_heatmap}, \ref{fig:rf_heatmap}, and \ref{fig:nn_heatmap} that ChatGPT is classified 100\% accurately by Random Forest and Neural Network, and is very close with K-Nearest Neighbors.
 
@@
 If all of our packets had their own protocols, we'd probably be able to use a simple decision tree with two splits and get nearly 100\% accuracy.
-In reality, the physical closeness of LinkedIn and Blackboard data made it hard for KNN to accurately guess based on neighbors, for the Random Forest to build meaningfully effective trees, and for the Neural Network to solve itself cleanly.
+In reality, the physical closeness of LinkedIn and Blackboard data made it hard for K-Nearest Neighbors to accurately guess based on neighbors, for the Random Forest to build meaningfully effective trees, and for the Neural Network to solve itself cleanly.
 
@@
 Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length.
-In figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.
-This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per figure \ref{fig:length_scatter}.
+In Figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.
+This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per Figure \ref{fig:length_scatter}.
 
@@
   \includegraphics[width=1\linewidth]{Figures_and_Graphs/PredictedPacketsScatterKNN.png}
-  \caption{KNN Predictions Scatterplot}
+  \caption{K-Nearest Neighbors Predictions Scatter plot}
   \label{fig:knn_scatter}
@@
   \includegraphics[width=1\linewidth]{Figures_and_Graphs/PredictedPacketsScatterRF.png}
-  \caption{Random Forest Predictions Scatterplot}
+  \caption{Random Forest Predictions Scatter plot}
   \label{fig:rf_scatter}

### 2024-05-05 Final_Report/paper.tex
added colon

@@
 using Wireshark, then the data was reformatted to eliminate bias and get more accurate results.
-Using the collected data we then trained four models which had varying levels of accuracy, Logistic Regression (56\%), 
+Using the collected data we then trained four models which had varying levels of accuracy: Logistic Regression (56\%), 
 K-Nearest Neighbors (77\%), Random Forest (83\%), and finally a neural

### 2024-05-05 Final_Report/paper.tex
fixed ml
fixed

@@
 % TODO fill in your paper title
-\newcommand{\PaperTitle}{Comparative Analysis of Machine Learning Algorithms for Website Traffic Classification from Network Packets }
+\newcommand{\PaperTitle}{Comparative Analysis of machine learning Algorithms for Website Traffic Classification from Network Packets }
 % TODO fill in your paper number when you get it
@@
 To commence the collection of our data, we open Wireshark and select a network connection. 
-In this project we established a connection the College of William and Mary's network interface (en0). In order to isolate the web traffic in order to specifically collect 
+In this project we established a connection to the College of William and Mary's network. In order to isolate the web traffic to specifically collect 
 packets that we are analyzing, the capture filter functionality is utilized.

### 2024-05-05 Final_Report/paper.tex
protocol

@@
 
-Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
+Consequently, the features selected for training and testing the models are time, length, and protocol. The protocol feature is converted to an integer for compatibility with 
 the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in Figure \ref{fig:webTraffic}.
@@
 
-First, as you can see from the Actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the Protocol feature.
+First, as you can see from the Actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the protocol feature.
 ChatGPT uses almost exclusively QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2.
@@
 
-Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length.
+Since protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length.
 In Figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.

### 2024-05-05 Final_Report/paper.tex
edits

--- 2024-05-05 Final_Report/paper.tex
@@
 using Wireshark, then the data was reformatted to eliminate bias and get more accurate results.
-Using the collected data we then trained four models which had varying levels of accuracy: Logistic Regression (56\%), 
+Using the collected data we then trained four models which had varying levels of accuracy, Logistic Regression (56\%), 
 K-Nearest Neighbors (77\%), Random Forest (83\%), and finally a neural
@@
 examining web traffic, especially in a scale as large as the internet. One example of our project's significance is that this can be crucial data analysis 
-for network administrators and security professionals, whom would examine the network for malicious traffic.
+for network administrators and security professionals, who would examine the network for malicious traffic.
 
@@
 
-  Traffic classification is very significant in practice, if done accurately and effectively \cite{10.1109/TNET.2014.2320577}.
+Traffic classification, if done accurately and effectively, is very significant in practice \cite{10.1109/TNET.2014.2320577}.
 For reasons mentioned previously, the observed capabilities of this and other projects
-  can be crucial for network administrators and security professionals, whom would examine the network for malicious traffic.
+can be crucial for network administrators and security professionals, who would examine the network for malicious traffic.
 
-  For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and LinkedIn.
-These sets were then merged into a single dataset, which was then split into training and validating sets.
+For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and 
+LinkedIn. These sets were then merged into a single dataset, which was then split into training and validating sets. 
 Four models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.
@@
 
-\subsubsection{Network analysis tool} For this project, the tool chosen and used was Wireshark \cite{Wireshark}, a widely used network protocol analyzer.
+\subsubsection{Network analysis tool} For this project, we chose to use Wireshark\cite{Wireshark}, a widely used network analysis tool.
 Wireshark is capable of capturing and analyzing network packets, and is able to provide a detailed
@@
 It shows the packet data in a human-readable format, and provides a detailed view of the packet's contents.
- This data contains information on time taken for packet to send and arrive, protocols used, size of each packet, and other fields such as more information on the packet and the source IP address.
+ This data contains information on the timestamp when the packet was recognized by Wireshark, protocols used, packet size, more information on the packet, and the source and destination IP addresses.
 This tool also supports use of different forms of link communication and can be specified to capture packets from a specific network interface (i.e.
@@
 As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
-Including these would be of course the simplest way to classify the data, of course, but the objective of this investigation is to have a highly applicable mechanism to classify network data when a small subset of information is available.
+Including these would of course be the simplest way to classify the data, but the objective of this investigation is to have a highly applicable mechanism to classify network data when a small subset of information is available.
 Including the dependent variable of the research question as an independent variable would trivialize the research.
@@
 There is no good reason to think this would help with classification, and even if it were to improve the accuracy with our test set, we have no ability to predict in good faith that this would always be the case, since there isn't a consistent semantic meaning.
+
+It's possible we could've examined all possible formats of this field to extract relevant information, but since we were classifying on a packet by packet basis, it would be difficult to have a consistent feature that captures this variance.
 

### 2024-05-05 Final_Report/paper.tex
edits

--- 2024-05-05 Final_Report/paper.tex
@@
 Consequently, the features selected for training and testing the models are time, length, and protocol. The protocol feature is converted to an integer for compatibility with 
-the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in Figure \ref{fig:webTraffic}.
+the models, using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in Figure \ref{fig:webTraffic}.
 Additionally, a categorical variable titled "Website"
-is created which displays which website the packet originated (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
+is created which displays from which website the packet originated  (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
 the models to detect relationships between the packets and their corresponding web traffic origin.
@@
 For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet.
-In the end, we chose to employ four different models: Logistic Regression K-Nearest Neighbors, Random Forest, and a Neural Network.
+In the end, we chose to employ four different models: Logistic Regression, K-Nearest Neighbors, Random Forest, and a Neural Network.
 The reason we selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution.
@@
 Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
-It was understood initially that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.
+It was understood initially that this model may not be an ideal fit for our data due to the regression's binary nature.
+Using a binary model while having more than two classifications in our data is not ideal.
 
@@
 \begin{enumerate}
-  \item \textbf{Binary Outcome}: Logistic regression is used for binary classification tasks, where the outcome variable has only two possible outcome
-  \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcome
-  \item \textbf{Probabilistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
+  \item \textbf{Binary Outcome}: Logistic regression is used for binary classification tasks, where the outcome variable has only two possible outcomes.
+  \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcomes.
+  \item \textbf{Probabilistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class.
   \item \textbf{Interpretability}: Logistic regression coefficients represent the change in the log-odds of the outcome for a one-unit change in the corresponding independent variable, making it easy to interpret the impact of each variable on the outcome.
-This characteristic was especially important for our baseline
+This characteristic was especially important for our baseline.
 \end{enumerate}
@@
 
-The execution of this model was rather simple: splitting the data into training and testing sets and executing a standard regression to be analyzed.
+The execution of this model was rather simple: splitting the data into training and testing sets and executing a standard regression.
 This simplistic approach, as previously mentioned, allowed for us to inspect which features were most advantageous for us and more importantly which features we would continue to analyze.

### 2024-05-05 Final_Report/paper.tex
edit
Fixed graphs
edits

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
+  \caption{Processed Web Traffic Data}
+  \label{fig:webTraffic}
+\end{figure*}
+
 \subsubsection{Data Formatting}
@@
 This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure \ref{fig:webTraffic} presents the refined data following the data preparation.
-
-\begin{figure*}[htp] 
-  \centering
-  \includegraphics[width=\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
-  \caption{Processed Web Traffic Data}
-  \label{fig:webTraffic}
-\end{figure*}
 
@@
 Using a binary model while having more than two classifications in our data is not ideal.
-
-\begin{figure}[!h]
-  \centering
-  \includegraphics[width=9cm]{Figures_and_Graphs/LogReg.png}
-  \caption{Logistic Regression model structure example}
-  \label{fig:RFExample}
-\end{figure}
 
@@
 based on their proximity to a specified number (k) of existing data points.
-\begin{figure}[htp] 
+\begin{figure}[!h]
   \centering
@@
 
-Advantages of Random Forest Models:
-\begin{enumerate}
-  \item \textbf{Ability to handle complex features}: Random forests have the ability to handle complex features, such as time and protocols in the case of network packets, and the relationships between them, which can be very important in classifying network traffic.
-  \item \textbf{High accuracy}: Random forests diminishes the problem of overfitting that can occur in decision trees, and can achieve higher accuracy, helping to more accurately determine website origins of a packet.
-  \item \textbf{Feature importance}: Random forests can provide insight into which features are most important in the classification process, such as protocol vs time in classifying websites for this project.
-  \item \textbf{Scalability}: Random forests can be scaled to handle much larger datasets, which can be very important for network traffic which can receive a high volume of packet data extremely quick.
-\end{enumerate}
-
 \begin{figure}[!h]
@@
 
+Advantages of Random Forest Models:
+\begin{enumerate}
+  \item \textbf{Ability to handle complex features}: Random forests have the ability to handle complex features, such as time and protocols in the case of network packets, and the relationships between them, which can be very important in classifying network traffic.
+  \item \textbf{High accuracy}: Random forests diminish the problem of overfitting that can occur in decision trees, and can achieve higher accuracy, helping to more accurately determine website origins of a packet.
+  \item \textbf{Feature importance}: Random forests can provide insight into which features are most important in the classification process, such as protocol vs time in classifying websites for this project.
+  \item \textbf{Scalability}: Random forests can be scaled to handle much larger datasets, which can be very important for network traffic which can receive a high volume of packet data extremely quickly.
+\end{enumerate}
+
 The library used for the Random Forest model was scikit-learn \cite{scikit-learn}.
-Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
+Sci-kit learn's implementation of Random Forests utilizes aggregation to take a soft vote of the soft classifications (probability of the packet being from each class).
 Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.
@@
 Within random forest models, many hyperparameters can be fine-tuned to optimize the model. For this project, we chose to optimize the hyperparameters for n estimators (number of trees in the forest), 
-max depth (maximum depth (levels) in the tree), and min samples split (minimum samples within a node to be able to split it into children).
+max depth (maximum depth in the tree), and min samples split (minimum samples a node must contain in order to split).
 In order to optimize all of these hyperparameters, we used a grid search to find the best combination of hyperparameters that would 
@@
 
-The final model we chose to use was a Neural Network.
-A Neural Network is a machine learning model that tries to make decision as if it were a human brain. 
+The final model we chose to use was a neural network.
+A neural network is a machine learning model that tries to make decision as if it were a human brain. 
 It consists of a graph of nodes, analogous to neurons, that are interconnected by directed edges, analogous to synapses.
@@
     In our case, since the model had three inputs, Time, Length, and Protocol, there were three nodes in the input layer.
-    \item {\bf Output Layer}: The output layer is the layer that makes the decisions as to what classes the data are places in.
+    \item {\bf Output Layer}: The output layer is the layer that makes the decisions as to what classes the data are placed in.
 In a "one-hot-encoding" scheme, which is what we employed, there are as many nodes as there are output classes in the data.
 For our purposes, this corresponds to three nodes, one for Blackboard, one for ChatGPT, and one for LinkedIn.
-One of the nodes is activated for each data point, and that is the class label it receives.
+One of the nodes is activated for each data point, and that is the class label that it receives.
     In binary classification data sets, you could use a single node, and define a threshold, before which the output is classified as class 0 and after which the output is classified as class 1.
@@
 
-In a fully-connected neural network, or multilayer perceptron (MLP), which is what our model used, all nodes in each layer of the topology are connected to every node in the next layer, and every node in the previous layer.
+In a fully-connected neural network, or multilayer perceptron (MLP), all nodes in each layer of the topology are connected to every node in the next and previous layer.
 Nodes at the same layer are not connected.
@@
 \ref{fig:nn}
-shows the topology and edge structure of an MLP with a 3 node input layer, like out model, a 1 node output layer, {\it unlike} our model, and two hidden layers with four nodes each.
+shows the topology and edge structure of an MLP with a three node input layer, like our model, a one node output layer, {\it unlike} our model, and two hidden layers with four nodes each.
 
@@
 Variables $w_i$ and $b$ correspond to weight and bias, respectively. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
-The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.
+The resulting value $z$ is the input to an {\it activation function}, which modifies and normalizes the output before it is passed to the next node.
 
@@
 
-After activation, the math at this node is finished, and the post activation output becomes the input from this node for all the nodes in hidden layer 2.
+After activation, the math at this node is finished, and the post activation output becomes the input from this node for all the nodes in hidden layer two.
 
-Through a solving process, the specific algorithm of which (lbfgs) will be passed into the model, 
-the weights and bias are all calculated for every node, in order to maximize accuracy.
+Through a solving algorithm passed into the model, the weights and bias are all calculated for every node, in order to maximize accuracy.
 
@@
 We ran a GridSearch on many possible combinations of parameters, exhaustively searching every combination.
-In order to do this, we used the \texttt{GridSearchCV} library in python from scikitlearn, which allowed us to divide the training data into 5 partitions.
+In order to do this, we used the \texttt{GridSearchCV} library in python from scikit-learn, which allowed us to divide the training data into 5 partitions.
 Then 5 separate times, each of the partitions could be used as the validation data, while the rest of the training data was used to solve the network.

### 2024-05-05 Final_Report/paper.tex
done

@@
 
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/LogReg.png}
+  \caption{Logistic Regression model structure example}
+  \label{fig:log_reg_example}
+\end{figure}
+
 Characteristics of Logistic Regression:
@@
 based on their proximity to a specified number (k) of existing data points.
+
 \begin{figure}[!h]
@@
 \end{enumerate}
-\begin{figure}
+\begin{figure}/
     \centering
@@
 \section{Evaluation}
-This section comprehensively evaluates our models and their performance on the dataset and validating sets.
-Later, goes on to determine the model which best classified our selected websites based on network packet data.
+This section comprehensively evaluates our models and their performance on the training and test sets.
+It also determines the model which best classified our selected websites based on network packet data.
 
@@
 First and foremost, we had completely separate training data and test data.
-The training data was used in training processes such as KFold validation that require it to be split "test"-train splits, but we refer to those "test" sets as validation sets, because they are part of the training process, and completely unrelated to the test data.
+The training data was used in training processes such as KFold validation that require it to be separated into "test"-train splits, but we refer to those "test" sets as validation sets, because they are part of the training process, and completely unrelated to the test data.
 
-Moreover, we used the same test data on all four models, in order to ensure an accurate comparison between them, since their performance is therefore measured with similar constraints.
+Moreover, we used the same test data on all four models, in order to ensure an accurate comparison between them, since their performance is measured with similar constraints.
 We also used the same training data for all four models, except in the Neural Network we collected and added additional data. This is because Neural networks tend to need more data on which to train.
@@
 
-Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.
+Macro F1 is the harmonic average of the precision and recall for every class, averaged across all classes.
 
 Recall is the calculation of how many the model correctly classified within a class (i.e. how many truly belong in that class in the entire dataset). 
-Precision is the calculation of how many the model correctly classified within a class (i.e. can be thought of as class accuracy).
+Precision is the calculation of how many the model correctly classified within a class. It can be thought of as class accuracy.
 
@@
 As you can see from the difference between the logistic regression scatter plot in Figure \ref{fig:log_reg_scatter} and the actual class scatter plot in Figure \ref{fig:actual_scatter}, it seems the classification grouped packets mostly based on the time variable, which didn't result in very accurate results.
-We'll get into the specifics of the time variable's specific limitations shortly.
+We'll get into the specifics of the time variable's limitations shortly.
 
-Beyond the baseline logistic regression model, the other models all perform fairly similarly, in the high 70s and low 80s in terms of test accuracy.
+Beyond the baseline logistic regression model, the other models all perform similarly, in the high 70s and low 80s in terms of test accuracy.
 These numbers are good, but not great, for a number of reasons.
 
-First, as you can see from the Actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the protocol feature.
-ChatGPT uses almost exclusively QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2.
-This makes differentiating ChatGPT from either of the others trivially easy, but disambiguating Blackboard and LinkedIn relatively hard.
+First, as you can see from the actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the protocol feature. 
+ChatGPT almost exclusively uses QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2.
+This makes differentiating ChatGPT from either of the others trivial, but disambiguating Blackboard and LinkedIn relatively hard.
 
@@
 
-If all of our packets had their own protocols, we'd probably be able to use a simple decision tree with two splits and get nearly 100\% accuracy.
-In reality, the physical closeness of LinkedIn and Blackboard data made it hard for K-Nearest Neighbors to accurately guess based on neighbors, for the Random Forest to build meaningfully effective trees, and for the Neural Network to solve itself cleanly.
+If all of our websites had their own protocols, we'd probably be able to use a simple decision tree with two splits and get nearly 100\% accuracy.
+In reality, the physical closeness of the LinkedIn and Blackboard data made it hard for K-Nearest Neighbors to accurately predict, for the Random Forest to build fully effective trees, and for the Neural Network to solve itself cleanly.
 
@@
 Since protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length.
-In Figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn.
+In Figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values than LinkedIn.
 This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per Figure \ref{fig:length_scatter}.
@@
 First and foremost, we'd want to use a more meaningful variable instead of the unadjusted Time field as one of our input features.
-While it's true that time could be more meaningful if there was a set length of time in which each session of Wireshark data, even controlling for that doesn't completely eliminate bias from the variable.
-A better approach would be to use time since previous packet, by getting the time field from the packet indexed before, and taking a difference, for every packet in the dataset (except the first, of course, which would have to be excluded).
-If we were to do this approach, there's potential that the variance of delays in packets, combined with the length variable which we'd still be measuring, would give our models information as to the amount of data transfer happening in the website, which could be explanatory towards its class.
+Time could be more meaningful if we had a set length of time in which each session of Wireshark data was acquired.
+However, even controlling for that doesn't completely eliminate bias from the variable. 
+A better approach would be to use "time-since-previous packet", by getting the time field from the packet indexed before, and taking a difference, for every packet in the dataset. 
+If we were to do this approach, there's potential that the variance of delays in packets, combined with the length variable which we'd still be measuring, would give our models information as to the amount of data transfer happening to and from the website.
+This could help with classification.
 
 Additionally, we would want to expand our dataset and collect data from more than three websites, with use cases across the Internet. 
-Perhaps if the model were trained on enough different types of sites, we'd be able to classify by website type, such as social media, shopping, etc.
+Perhaps if the model were trained on many different types of sites, we'd be able to classify by website type, such as social media, shopping, etc.
 Then maybe the model would even be applicable to more domains that weren't even visited in the training data.
@@
 This would give us access to more independent variables, such as average length, average packet delay, etc.
-Since network communication is a constant flow of packets, it's possible that zooming out in this way from the way our model is currently would provide more explanatory power.
+Since network communication is a constant flow of packets, it's possible that zooming out from our current implementation would produce stronger predictions.
 
 \section{Conclusion}
-This project explored developing and evaluating models that could classify network traffic by its originating source website. Gathering datasets from three websites:
-ChatGPT, LinkedIn, and Blackboard we then developed 4 models: Logistic Regression, K-Nearest Neighbors, Random Forest, and a Neural Network.
-After thorough evaluation, the neural network was noticeably outperforming the other three as it achieved the highest accuracy and Macro F1 scores.
+This project explored developing and evaluating models that could classify network traffic by its originating source website. After gathering datasets from three websites,
+ChatGPT, LinkedIn, and Blackboard, we then developed 4 models: Logistic Regression, K-Nearest Neighbors, Random Forest, and a Neural Network.
+After thorough evaluation, the neural network outperformed the other three as it achieved the highest accuracy and Macro F1 scores.
 
 Our work shows the applications and potential of machine learning in network traffic analysis.
-The models developed in this project could be used in real-world applications to help network administrators and security professionals in detecting and preventing malicious activities on their networks.
-This would effectively help them to manage the overall network performance and security, and ensure the network is operating as intended.
+The models developed in this project could be used in real-world applications to help network administrators and security professionals in detecting and preventing malicious activities on their networks, and help them to manage its overall performance and security.
 
@@
   \item The project's results indicate the significance of feature selection and data set size in order to effectively and accurately classify network traffic.
-  \item The graphs, maps, and other visuals help to display each models' predictability towards actual website targets and helps to see the effectiveness of each. 
+  \item The graphs, maps, and other visuals help to display each models' predictability towards actual website targets and help to see the effectiveness of each. 
 \end{enumerate}
